---
title: "Appendix B"
subtitle: "Study 2 - Attention Bias Manipulation"
author: "MM"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
  html_notebook: 
    toc: true
runtime: markdown
editor_options:
  markdown:
    wrap: 72
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	eval = TRUE,
	message = FALSE,
	warning = FALSE,
	digits = 3
)
# Load libraries
library(rmarkdown)
library(shiny)

library(readxl) # For reading excel files
library(dplyr) # For reshaping and summarizing data

library(ggplot2) # For plots
library(gridExtra) # For arranging ggplots in a grid
library(grid) # For grob functions
library(sjPlot) # For plotting interactions
library(ggeffects) # For plotting gamlss

library(psych) # For Cronbach's alpha and McDonald's omega
library(car) # For inverse logit function
library(pastecs) # For testing normality assumptions

library(gamlss) # For gamlss fitting
library(lme4) # For lmm fitting
library(lmtest) # For likelihood ratio tests
library(boot) # For inverse logit function
```

![](images\study2\procedure_study2.svg)

# Data Preparation

This section documents the main preprocessing steps used to derive the variables analyzed in Study 2. Consistent with the manuscript, data preparation for perfectionism and attentional measures followed the same procedures as in Study 1. This section therefore focuses on the Study 2-specific extensions, namely (a) repeated mood assessments, (b) pre–post attentional data, and (c) construction of change scores.

## Questionnaire data

Perfectionism was assessed using the Hewitt and Flett Multidimensional Perfectionism Scale (HMPS) and the Frost Multidimensional Perfectionism Scale (FMPS). As in Study 1, item scoring, reverse coding, and computation of questionnaire totals followed the standard scoring procedures for each instrument.

Psychological distress was assessed repeatedly using seven Visual Analog Mood Scales (VAMS; 0–100). In line with the manuscript, these items were aggregated into Positive Mood (happy, excited, positive mood) and Negative Mood (sad, anxious, angry, negative mood) scores. Baseline depressive and anxiety symptoms were assessed using the CES-D and GAD-7 and were retained as control variables.


```{r read_data_questionnaires_study2, include=FALSE}
# Read data
qu2.1 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.1.xlsx")
qu2.2 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.2.xlsx")
qu2.3_1 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_1.xlsx")
qu2.3_2 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_2.xlsx")
qu2.3_3 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_3.xlsx")

# Merge questionnaire files
qu2a <- qu2.1 %>% inner_join(qu2.2, by = "ID")
qu2b <- qu2.3_1 %>% inner_join(qu2.3_2, by = "ID") %>% inner_join(qu2.3_3, by = "ID")
qu2 <- qu2a %>% inner_join(qu2b, by = "ID")
```

  
```{r qu_scores_study2}
# HMPS reverse coding
qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_8", "HMPS_9", "HMPS_10", "HMPS_12",
        "HMPS_19", "HMPS_21", "HMPS_24", "HMPS_30", "HMPS_34", "HMPS_36", "HMPS_37",
        "HMPS_38", "HMPS_43", "HMPS_44", "HMPS_45")] <-
  8 - qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_8", "HMPS_9", "HMPS_10", "HMPS_12",
              "HMPS_19", "HMPS_21", "HMPS_24", "HMPS_30", "HMPS_34", "HMPS_36", "HMPS_37",
              "HMPS_38", "HMPS_43", "HMPS_44", "HMPS_45")]

# HMPS subscales
SOP <- qu2[, c("HMPS_1", "HMPS_6", "HMPS_8", "HMPS_12", "HMPS_14", "HMPS_15", "HMPS_17",
               "HMPS_20", "HMPS_23", "HMPS_28", "HMPS_32", "HMPS_34", "HMPS_36", "HMPS_40", "HMPS_42")]
OOP <- qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_7", "HMPS_10", "HMPS_16", "HMPS_19",
               "HMPS_22", "HMPS_24", "HMPS_26", "HMPS_27", "HMPS_29", "HMPS_38", "HMPS_43", "HMPS_45")]
SPP <- qu2[, c("HMPS_5", "HMPS_9", "HMPS_11", "HMPS_13", "HMPS_18", "HMPS_21", "HMPS_25",
               "HMPS_30", "HMPS_31", "HMPS_33", "HMPS_35", "HMPS_37", "HMPS_39", "HMPS_41", "HMPS_44")]

qu2$SOP <- rowSums(SOP)
qu2$OOP <- rowSums(OOP)
qu2$SPP <- rowSums(SPP)

# FMPS subscales
PS <- qu2[, c("FMPS_4", "FMPS_6", "FMPS_12", "FMPS_16", "FMPS_19", "FMPS_24", "FMPS_30")]
PE <- qu2[, c("FMPS_1", "FMPS_11", "FMPS_15", "FMPS_20", "FMPS_26")]
PC <- qu2[, c("FMPS_3", "FMPS_5", "FMPS_22", "FMPS_35")]
CM <- qu2[, c("FMPS_9", "FMPS_10", "FMPS_13", "FMPS_14", "FMPS_18", "FMPS_21", "FMPS_23", "FMPS_25", "FMPS_34")]
DA <- qu2[, c("FMPS_17", "FMPS_28", "FMPS_32", "FMPS_33")]
O  <- qu2[, c("FMPS_2", "FMPS_7", "FMPS_8", "FMPS_27", "FMPS_29", "FMPS_31")]

qu2$PS <- rowSums(PS)
qu2$PE <- rowSums(PE)
qu2$PC <- rowSums(PC)
qu2$CM <- rowSums(CM)
qu2$DA <- rowSums(DA)
qu2$O  <- rowSums(O)

# VAMS composites
POS_1 <- qu2[, c("VAMS1_1", "VAMS1_6", "VAMS1_7")]
NEG_1 <- qu2[, c("VAMS1_2", "VAMS1_3", "VAMS1_4", "VAMS1_5")]
POS_2 <- qu2[, c("VAMS2_1", "VAMS2_6", "VAMS2_7")]
NEG_2 <- qu2[, c("VAMS2_2", "VAMS2_3", "VAMS2_4", "VAMS2_5")]
POS_3 <- qu2[, c("VAMS3_1", "VAMS3_6", "VAMS3_7")]
NEG_3 <- qu2[, c("VAMS3_2", "VAMS3_3", "VAMS3_4", "VAMS3_5")]
POS_4 <- qu2[, c("VAMS4_1", "VAMS4_6", "VAMS4_7")]
NEG_4 <- qu2[, c("VAMS4_2", "VAMS4_3", "VAMS4_4", "VAMS4_5")]

qu2$POS_1 <- rowSums(POS_1)
qu2$NEG_1 <- rowSums(NEG_1)
qu2$POS_2 <- rowSums(POS_2)
qu2$NEG_2 <- rowSums(NEG_2)
qu2$POS_3 <- rowSums(POS_3)
qu2$NEG_3 <- rowSums(NEG_3)
qu2$POS_4 <- rowSums(POS_4)
qu2$NEG_4 <- rowSums(NEG_4)

# CES-D reverse coding and totals
qu2[, c("CESD_4", "CESD_8", "CESD_12", "CESD_16")] <-
  3 - qu2[, c("CESD_4", "CESD_8", "CESD_12", "CESD_16")]

CESD <- qu2[, c("CESD_1", "CESD_2", "CESD_3", "CESD_4", "CESD_5", "CESD_6", "CESD_7", "CESD_8",
                "CESD_9", "CESD_10", "CESD_11", "CESD_12", "CESD_13", "CESD_14", "CESD_15",
                "CESD_16", "CESD_17", "CESD_18", "CESD_19", "CESD_20")]
qu2$CESD <- rowSums(CESD)

# GAD-7 totals
qu2$GAD7_1 <- as.numeric(qu2$GAD7_1)
qu2$GAD7_2 <- as.numeric(qu2$GAD7_2)
qu2$GAD7_3 <- as.numeric(qu2$GAD7_3)
qu2$GAD7_4 <- as.numeric(qu2$GAD7_4)
qu2$GAD7_5 <- as.numeric(qu2$GAD7_5)
qu2$GAD7_6 <- as.numeric(qu2$GAD7_6)
qu2$GAD7_7 <- as.numeric(qu2$GAD7_7)

GAD7 <- qu2[, c("GAD7_1", "GAD7_2", "GAD7_3", "GAD7_4", "GAD7_5", "GAD7_6", "GAD7_7")]
qu2$GAD7 <- rowSums(GAD7)
```


### Outlier Handling

Outliers were identified before computing descriptive statistics and correlations. Following the same procedure as in Study 1, univariate outliers were defined as observations with standardized scores below -3 or above +3, and multivariate outliers were assessed using Mahalanobis distance. 

```{r boxplots_study2, fig.width = 18, fig.height= 8}
par(mfrow=c(1,2))
boxplot(qu2[, c("SOP", "OOP","SPP", "PS", "PC", "PE", "CM", "DA", "O", "CESD", "GAD7")])
boxplot(qu2[, c("POS_1", "NEG_1", "POS_2", "NEG_2","POS_3", "NEG_3", "POS_4", "NEG_4")])
```

```{r outliers_study2}
# Standardize questionnaire variables
qu2[, c("ZSOP", "ZOOP", "ZSPP", "ZPS", "ZPC", "ZPE", "ZCM", "ZDA", "ZO", "ZGAD7", "ZCESD",
        "ZPOS_1", "ZNEG_1", "ZPOS_2", "ZNEG_2", "ZPOS_3", "ZNEG_3", "ZPOS_4", "ZNEG_4")] <-
  scale(qu2[, c("SOP", "OOP", "SPP", "PS", "PC", "PE", "CM", "DA", "O", "GAD7", "CESD",
                "POS_1", "NEG_1", "POS_2", "NEG_2", "POS_3", "NEG_3", "POS_4", "NEG_4")])

# Identify univariate outliers
univar_out <- c(
  which(qu2$ZSOP > 3 | qu2$ZSOP < -3),
  which(qu2$ZOOP > 3 | qu2$ZOOP < -3),
  which(qu2$ZSPP > 3 | qu2$ZSPP < -3),
  which(qu2$ZPS > 3 | qu2$ZPS < -3),
  which(qu2$ZPE > 3 | qu2$ZPE < -3),
  which(qu2$ZPC > 3 | qu2$ZPC < -3),
  which(qu2$ZCM > 3 | qu2$ZCM < -3),
  which(qu2$ZDA > 3 | qu2$ZDA < -3),
  which(qu2$ZO > 3 | qu2$ZO < -3),
  which(qu2$ZGAD7 > 3 | qu2$ZGAD7 < -3),
  which(qu2$ZCESD > 3 | qu2$ZCESD < -3),
  which(qu2$ZPOS_1 > 3 | qu2$ZPOS_1 < -3),
  which(qu2$ZNEG_1 > 3 | qu2$ZNEG_1 < -3),
  which(qu2$ZPOS_2 > 3 | qu2$ZPOS_2 < -3),
  which(qu2$ZNEG_2 > 3 | qu2$ZNEG_2 < -3),
  which(qu2$ZPOS_3 > 3 | qu2$ZPOS_3 < -3),
  which(qu2$ZNEG_3 > 3 | qu2$ZNEG_3 < -3),
  which(qu2$ZPOS_4 > 3 | qu2$ZPOS_4 < -3),
  which(qu2$ZNEG_4 > 3 | qu2$ZNEG_4 < -3)
)

univar_out <- unique(univar_out)

# Remove univariate outliers
qu2 <- qu2[-univar_out, ]

# Identify multivariate outliers
vars <- qu2[, c("SOP", "OOP", "SPP", "PS", "PC", "PE", "CM", "DA", "O",
                "POS_1", "NEG_1", "POS_2", "NEG_2", "POS_3", "NEG_3", "POS_4", "NEG_4")]
md <- mahalanobis(vars, center = colMeans(vars), cov = cov(vars))
cutoff <- qchisq(p = 1 - .001, df = ncol(vars))
multivar_out_MH <- which(md > cutoff)

length(multivar_out_MH)

# Remove one participant flagged administratively as outlier in the condition variable
which(qu2$Condition == "Outlier")
qu2 <- qu2[-which(qu2$Condition == "Outlier"), ]
```

Univariate outliers were excluded from subsequent analyses. No multivariate outliers were identified.

### Perfectionism Dimensions

Following the same procedure as in Study 1, Perfectionistic Strivings was computed as the sum of standardized Personal Standards (FMPS-PS) and Self-Oriented Perfectionism (HMPS-SOP) scores. Perfectionistic Concerns was computed as the sum of standardized Concerns over Mistakes (FMPS-CM), Doubts about Actions (FMPS-DA), and Socially Prescribed Perfectionism (HMPS-SPP) scores.
        
```{r strivings_concerns_study2}
qu2$Perf_Strivings <- rowSums(qu2[, c("ZPS", "ZSOP")])
qu2$Perf_Concerns  <- rowSums(qu2[, c("ZCM", "ZDA", "ZSPP")])
```

### Mood Change Scores

Psychological distress was operationalized as change in emotional state from before to after the Tangram task. Positive and negative emotion scores were computed as sums of the corresponding VAMS items, and change scores were calculated by subtracting pre-task from post-task values.

Additional post–pre difference scores were also computed to describe changes following the ABM task.

Prior to computing change scores, positive and negative mood composites were standardized at each assessment wave. This was done to reduce skewness in the mood variables and to express pre–post change relative to the distribution of scores at each time point, thereby reducing dependence on wave-specific differences in scale and dispersion.

```{r}
# Standardize repeated mood scores before computing change indices
qu2[, c("ZPOS_2", "ZPOS_3", "ZPOS_4", "ZNEG_2", "ZNEG_3", "ZNEG_4")] <-
  scale(qu2[, c("POS_2", "POS_3", "POS_4", "NEG_2", "NEG_3", "NEG_4")])

# ABM-related change
qu2$POS_23 <- qu2$ZPOS_3 - qu2$ZPOS_2
qu2$NEG_23 <- qu2$ZNEG_3 - qu2$ZNEG_2

# Tangram-related change
qu2$POS_34 <- qu2$ZPOS_4 - qu2$ZPOS_3
qu2$NEG_34 <- qu2$ZNEG_4 - qu2$ZNEG_3
```


Descriptive statistics, zero-order correlations, and reliability coefficients for the questionnaire variables were computed after these preprocessing steps.

```{r descriptives_questionnaires_study2}
# Reliability estimates
alphaSOP <- psych::alpha(SOP)
omegaSOP <- psych::omega(SOP, plot = FALSE)
alphaOOP <- psych::alpha(OOP)
omegaOOP <- psych::omega(OOP, plot = FALSE)
alphaSPP <- psych::alpha(SPP)
omegaSPP <- psych::omega(SPP, plot = FALSE)

alphaPS <- psych::alpha(PS)
omegaPS <- psych::omega(PS, plot = FALSE)
alphaPE <- psych::alpha(PE)
omegaPE <- psych::omega(PE, plot = FALSE)
alphaPC <- psych::alpha(PC)
omegaPC <- psych::omega(PC, plot = FALSE)
alphaCM <- psych::alpha(CM)
omegaCM <- psych::omega(CM, plot = FALSE)
alphaDA <- psych::alpha(DA)
omegaDA <- psych::omega(DA, plot = FALSE)
alphaO  <- psych::alpha(O)
omegaO  <- psych::omega(O, plot = FALSE)

alphaPerf_Strivings <- psych::alpha(qu2[, c("ZPS", "ZSOP")])
alphaPerf_Concerns  <- psych::alpha(qu2[, c("ZCM", "ZDA", "ZSPP")])

alphaPOS_1 <- psych::alpha(POS_1)
omegaPOS_1 <- psych::omega(POS_1, plot = FALSE)
alphaNEG_1 <- psych::alpha(NEG_1)
omegaNEG_1 <- psych::omega(NEG_1, plot = FALSE)

alphaPOS_2 <- psych::alpha(POS_2)
omegaPOS_2 <- psych::omega(POS_2, plot = FALSE)
alphaNEG_2 <- psych::alpha(NEG_2)
omegaNEG_2 <- psych::omega(NEG_2, plot = FALSE)

alphaPOS_3 <- psych::alpha(POS_3)
omegaPOS_3 <- psych::omega(POS_3, plot = FALSE)
alphaNEG_3 <- psych::alpha(NEG_3)
omegaNEG_3 <- psych::omega(NEG_3, plot = FALSE)

alphaPOS_4 <- psych::alpha(POS_4)
omegaPOS_4 <- psych::omega(POS_4, plot = FALSE)
alphaNEG_4 <- psych::alpha(NEG_4)
omegaNEG_4 <- psych::omega(NEG_4, plot = FALSE)

alphaGAD7 <- psych::alpha(GAD7)
omegaGAD7 <- psych::omega(GAD7, plot = FALSE)
alphaCESD <- psych::alpha(CESD)
omegaCESD <- psych::omega(CESD, plot = FALSE)

# Descriptive statistics
round(describe(qu2[c("SOP", "OOP", "SPP", "PS", "PE", "PC", "CM", "DA", "O",
                     "Perf_Strivings", "Perf_Concerns",
                     "POS_23", "NEG_23", "POS_34", "NEG_34", "CESD", "GAD7")]), 2)

# Correlations
corr_table <- corr.test(qu2[c("Perf_Strivings", "Perf_Concerns",
                              "POS_23", "NEG_23", "POS_34", "NEG_34", "CESD", "GAD7")])$stars
print(corr_table)
```

## Attention Bias Measurement

Attentional data were collected at two time points, before (t1) and after (t2) the ABM procedure. As in Study 1, attention bias was assessed using the FV-FICB task with word stimuli from five semantic categories: Success, Failure, Positive, Negative, and Neutral.

### Response Times

Response times were defined as the latency between onset of the changed display and the participant’s response. Analyses were conducted on correct trials only, and trials with response times below 200 ms were excluded.

```{r read_data_rt_study2, include=FALSE}
rt2 <- read_excel("AB_Perfectionism_Data/rt_study2.xlsx")
```

### Correct Responses

Correct responses were recorded when participants accurately identified the changed word.

```{r data_preparation_rt_study2}
rt2$correct_response <- as.factor(rt2$correct_response) %>%
  dplyr::recode("Vrai" = 1, "Faux" = 0)

correct_responses <- rt2[,c("subject_nr", "correct_response", "Temps_de_mesure")] %>% group_by(subject_nr, Temps_de_mesure) %>% summarize(correct_response = sum(correct_response))

incorrect <- which(rt2$correct_response == 0)
rt200 <- which(rt2$response_time < 200)

length(incorrect)
length(rt200)

rt2$response_time[c(incorrect, rt200)] <- NA
```

Rule awareness was assessed at the end of each block and coded as a binary variable (0 = no, 1 = yes). This variable was used in subsequent analyses as a control and to derive pre–post rule-awareness change scores.

```{r guessed_block_rule_study2}
 rt2 <- rt2 %>% rename(guessed_block_rule = response_keyboard_response)
rt2$guessed_block_rule <- as.factor(rt2$guessed_block_rule) %>%
  dplyr::recode("o" = 1, "O" = 1, "n" = 0, "N" = 0)
```

For manipulation checks, response-time data were reshaped to a paired t1–t2 format and difference scores were computed as post-ABM minus pre-ABM values.

```{r short_format_rt_study2}
 t1 <- which(rt2$Temps_de_mesure == "T1")
t2 <- which(rt2$Temps_de_mesure == "T2")

rt2_1 <- rt2[t1, ]
rt2_2 <- rt2[t2, ]

drop <- c("Temps_de_mesure", "ID", "datetime", "response_position", "participant_response", "correct_response")

rt2_1 <- rt2_1[, !(names(rt2_1) %in% drop)] %>%
  rename(subject_nr_1 = subject_nr,
         response_time_1 = response_time,
         guessed_block_rule_1 = guessed_block_rule)

rt2_2 <- rt2_2[, !(names(rt2_2) %in% drop)] %>%
  rename(subject_nr_2 = subject_nr,
         response_time_2 = response_time,
         guessed_block_rule_2 = guessed_block_rule)

rt <- rt2_1 %>%
  inner_join(
    rt2_2,
    by = c("Code", "Change_category", "Change_location", "Change_word", "Flicker_word",
           "A", "B", "C", "D", "E",
           "OS_A_word", "OS_B_word", "OS_C_word", "OS_D_word", "OS_E_word",
           "CS_A_word", "CS_B_word", "CS_C_word", "CS_D_word", "CS_E_word", "block_loop")
  )

rt$response_time_diff <- rt$response_time_2 - rt$response_time_1
```


Descriptive statistics for response times were calculated after merging with questionnaire data.

```{r merge_rt_qu_study2, include = FALSE}
# Merge rt data with questionnaire data
rt_qu2 <- rt[c("Code",  "block_loop", "Change_category",
               "subject_nr_1","response_time_1", "guessed_block_rule_1", 
               "subject_nr_2","response_time_2", "guessed_block_rule_2", 
               "response_time_diff")]  %>% 
  rename(ID = Code) %>%
  inner_join(qu2[c("ID", "Condition", "Perf_Strivings", "Perf_Concerns",
                   "POS_23", "NEG_23", "POS_34", "NEG_34", "CESD", "GAD7",
                   "Age", "Sexe", "Statut","Actual_Studies","University_HE",
                   "Actual_Program","DomaineTravail", "Mother_Tongue")], 
             relationship = "many-to-many")
```

```{r descriptives_rt_study2}
# demographics
rt_qu2$Sexe <- as.factor(rt_qu2$Sexe) %>% dplyr::recode("Femme\r\n" = 0, "Homme\r\n" = 1)
sex <- rt_qu2[c("subject_nr_1", "Sexe")] %>% group_by(subject_nr_1) %>% summarise(Sexe = mean(Sexe))
sex$Sexe <- as.factor(sex$Sexe) %>% dplyr::recode("0" = "Female", "1" = "Male")
table(sex$Sexe)

round(describe(as.numeric(rt_qu2$Age)), 2)

# response time
round(describe(rt_qu2[c("response_time_1", "response_time_2", "response_time_diff")]), 2)

rt_qu2[c("Change_category", "response_time_1", "response_time_2", "response_time_diff")] %>%
  group_by(Change_category) %>%
  summarise(
    M_response_time_1 = round(mean(response_time_1, na.rm = TRUE), 2),
    SD_response_time_1 = round(sd(response_time_1, na.rm = TRUE), 2),
    M_response_time_2 = round(mean(response_time_2, na.rm = TRUE), 2),
    SD_response_time_2 = round(sd(response_time_2, na.rm = TRUE), 2),
    M_response_time_diff = round(mean(response_time_diff, na.rm = TRUE), 2),
    SD_response_time_diff = round(sd(response_time_diff, na.rm = TRUE), 2)
  )
```


### Eye Tracking

Eye movements during the free-viewing phase were used to compute the attentional indices. As in Study 1, raw eye-tracking data were recoded prior to index construction, and indices were aggregated at the block level.

```{r read_data_et_study2, include=FALSE}
et2 <- read_excel("AB_Perfectionism_Data/et_study2_500to5500.xlsx")
#for merging later
et2 <- et2 %>% rename(subject_nr = RECORDING_SESSION_LABEL)
```

```{r data_preparation_et_study2, include=FALSE}
et2$IA_LABEL <- as.factor(et2$IA_LABEL)
et2$IA_LABEL <- et2$IA_LABEL %>%
  dplyr::recode("Neutre" = "Neutral",
                "Pos" = "Positive",
                "Neg" = "Negative",
                "Pos_Perf" = "Success",
                "Neg_Perf" = "Failure")

et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- as.factor(et2$IA_FIRST_FIXATION_VISITED_IA_COUNT)
et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- et2$IA_FIRST_FIXATION_VISITED_IA_COUNT %>%
  dplyr::recode("0" = "1", "1" = "1", "2" = "0", "3" = "0", "4" = "0")
et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- as.numeric(as.character(et2$IA_FIRST_FIXATION_VISITED_IA_COUNT))

et2$IA_FIRST_FIXATION_TIME <- as.numeric(et2$IA_FIRST_FIXATION_TIME)
```

As in Study 1, the following block-level indices were derived: probability of first or second fixation, latency to first fixation, and dwell time. Dwell time was computed for the whole trial and separately for the early, intermediate, and late viewing phases.

```{r calculate_et_indices_study2}
# Merge ET with RT to recover block-level rule variables
et2$response_time <- as.numeric(et2$response_time)
etrt2 <- et2 %>% inner_join(rt2, relationship = "many-to-many")

et2a <- etrt2[c("Temps_de_mesure", "Code", "subject_nr", "block_loop", "IA_LABEL", "Change_category", "guessed_block_rule",
                "IA_DWELL_TIME", "IA_DWELL_TIME_500to1500", "IA_DWELL_TIME_1500to3500", "IA_DWELL_TIME_3500to5500",
                "IA_FIRST_FIXATION_VISITED_IA_COUNT", "IA_FIRST_FIXATION_TIME")] %>%
  group_by(Temps_de_mesure, Code, subject_nr, block_loop, IA_LABEL, Change_category, guessed_block_rule) %>%
  reframe(
    IA_FIRST_FIXATION_PROBABILITY = mean(na.omit(IA_FIRST_FIXATION_VISITED_IA_COUNT)),
    IA_FIRST_FIXATION_TIME_BLOCKMEAN = mean(na.omit(IA_FIRST_FIXATION_TIME)),
    IA_DWELL_TIME_BLOCKMEAN = mean(IA_DWELL_TIME),
    IA_DWELL_TIME_500to1500_BLOCKMEAN = mean(IA_DWELL_TIME_500to1500),
    IA_DWELL_TIME_1500to3500_BLOCKMEAN = mean(IA_DWELL_TIME_1500to3500),
    IA_DWELL_TIME_3500to5500_BLOCKMEAN = mean(IA_DWELL_TIME_3500to5500)
  )

et2b <- et2a %>%
  group_by(subject_nr, block_loop) %>%
  summarise(
    AVG_FIRST_FIXATION_TIME = sum(na.omit(IA_FIRST_FIXATION_TIME_BLOCKMEAN)),
    AVG_DWELL_TIME = sum(IA_DWELL_TIME_BLOCKMEAN),
    AVG_DWELL_TIME_500to1500 = sum(IA_DWELL_TIME_500to1500_BLOCKMEAN),
    AVG_DWELL_TIME_1500to3500 = sum(IA_DWELL_TIME_1500to3500_BLOCKMEAN),
    AVG_DWELL_TIME_3500to5500 = sum(IA_DWELL_TIME_3500to5500_BLOCKMEAN)
  )

et2 <- et2a %>% inner_join(et2b, relationship = "many-to-many")

et2$first_fix_prob <- et2$IA_FIRST_FIXATION_PROBABILITY
et2$first_fix_latency <- et2$IA_FIRST_FIXATION_TIME_BLOCKMEAN / et2$AVG_FIRST_FIXATION_TIME
et2$dwell_time <- et2$IA_DWELL_TIME_BLOCKMEAN / et2$AVG_DWELL_TIME
et2$dwell_time_early <- et2$IA_DWELL_TIME_500to1500_BLOCKMEAN / et2$AVG_DWELL_TIME_500to1500
et2$dwell_time_intermediate <- et2$IA_DWELL_TIME_1500to3500_BLOCKMEAN / et2$AVG_DWELL_TIME_1500to3500
et2$dwell_time_late <- et2$IA_DWELL_TIME_3500to5500_BLOCKMEAN / et2$AVG_DWELL_TIME_3500to5500
```


```{r remove_missing_et_study2}
# Remove remaining missing values
missing_ffp2 <- which(is.na(et2$first_fix_prob))
missing_ffl2 <- which(is.na(et2$first_fix_latency))
missing_dte2 <- which(is.na(et2$dwell_time_early))
missing_dtl2 <- which(is.na(et2$dwell_time_late))

et2 <- et2[-unique(c(missing_ffp2, missing_ffl2, missing_dte2, missing_dtl2)), ]
```

For manipulation checks, eye-tracking data were reshaped to paired t1–t2 format and post–pre difference scores were computed.

```{r short_format_et_study2}
t1 <- which(et2$Temps_de_mesure == "T1")
t2 <- which(et2$Temps_de_mesure == "T2")

et2_1 <- et2[t1, ]
et2_2 <- et2[t2, ]

et2_1 <- et2_1[c("Code", "subject_nr", "block_loop", "IA_LABEL", "Change_category",
                 "guessed_block_rule", "first_fix_prob", "first_fix_latency", "dwell_time",
                 "dwell_time_early", "dwell_time_intermediate", "dwell_time_late")] %>%
  rename(subject_nr_1 = subject_nr,
         first_fix_prob_1 = first_fix_prob,
         first_fix_latency_1 = first_fix_latency,
         dwell_time_1 = dwell_time,
         dwell_time_early_1 = dwell_time_early,
         dwell_time_intermediate_1 = dwell_time_intermediate,
         dwell_time_late_1 = dwell_time_late,
         guessed_block_rule_1 = guessed_block_rule)

et2_2 <- et2_2[c("Code", "subject_nr", "block_loop", "IA_LABEL", "Change_category",
                 "guessed_block_rule", "first_fix_prob", "first_fix_latency", "dwell_time",
                 "dwell_time_early", "dwell_time_intermediate", "dwell_time_late")] %>%
  rename(subject_nr_2 = subject_nr,
         first_fix_prob_2 = first_fix_prob,
         first_fix_latency_2 = first_fix_latency,
         dwell_time_2 = dwell_time,
         dwell_time_early_2 = dwell_time_early,
         dwell_time_intermediate_2 = dwell_time_intermediate,
         dwell_time_late_2 = dwell_time_late,
         guessed_block_rule_2 = guessed_block_rule)

et <- et2_1 %>% inner_join(et2_2, by = c("Code", "block_loop", "IA_LABEL", "Change_category"))

et$first_fix_prob_diff <- et$first_fix_prob_2 - et$first_fix_prob_1
et$first_fix_latency_diff <- et$first_fix_latency_2 - et$first_fix_latency_1
et$dwell_time_diff <- et$dwell_time_2 - et$dwell_time_1
et$dwell_time_early_diff <- et$dwell_time_early_2 - et$dwell_time_early_1
et$dwell_time_intermediate_diff <- et$dwell_time_intermediate_2 - et$dwell_time_intermediate_1
et$dwell_time_late_diff <- et$dwell_time_late_2 - et$dwell_time_late_1
```

Descriptive statistics for eye-tracking indices were calculated after merging with questionnaire data.

```{r merge_et_qu_study2, include=FALSE}
et_qu2 <- et %>%
  rename(ID = Code) %>%
  inner_join(
    qu2[c("ID", "Condition", "Perf_Strivings", "Perf_Concerns",
          "POS_23", "NEG_23", "POS_34", "NEG_34", "CESD", "GAD7",
          "Age", "Sexe", "Statut", "Actual_Studies", "University_HE",
          "Actual_Program", "DomaineTravail", "Mother_Tongue")],
    relationship = "many-to-many"
  )
```


```{r descriptives_et_indices_study2}
round(describe(et_qu2[c("first_fix_prob_1", "first_fix_latency_1", "dwell_time_1",
                        "dwell_time_early_1", "dwell_time_intermediate_1", "dwell_time_late_1")]), 2)

round(describe(et_qu2[c("first_fix_prob_2", "first_fix_latency_2", "dwell_time_2",
                        "dwell_time_early_2", "dwell_time_intermediate_2", "dwell_time_late_2")]), 2)

round(describe(et_qu2[c("first_fix_prob_diff", "first_fix_latency_diff", "dwell_time_diff",
                        "dwell_time_early_diff", "dwell_time_intermediate_diff", "dwell_time_late_diff")]), 2)
```

## Descriptive Statistics for Task Performance

### Response Accuracy

Response accuracy was defined as the number of trials in which the changed word was correctly identified. Descriptive statistics were computed separately for the pre-ABM (t1) and post-ABM (t2) assessments.

```{r descriptives_response_accuracy_study2}
accuracy <- correct_responses %>% group_by(subject_nr, Temps_de_mesure) %>% summarize(correct_response = sum(correct_response))

accuracy_1 <- accuracy$correct_response[correct_responses$Temps_de_mesure=='T1']
accuracy_2 <- accuracy$correct_response[correct_responses$Temps_de_mesure=='T2']

describe(accuracy_1)
describe(accuracy_2)
```

### Rule Awareness

Rule awareness was assessed at the end of each block and coded as a binary variable (0 = no, 1 = yes). For descriptive purposes, block-level responses were summed within time point, yielding the number of blocks in which participants reported awareness of the rule at t1 and t2.

```{r descriptives_rule_awareness_study2}
rule_awareness <- rt2 %>%
  group_by(subject_nr, block_loop, Temps_de_mesure) %>%
  summarise(guessed_block_rule = mean(as.numeric(as.character(guessed_block_rule))), .groups = "drop") %>%
  group_by(subject_nr, Temps_de_mesure) %>%
  summarise(guessed_block_rule = sum(guessed_block_rule), .groups = "drop")

rule_awareness_1 <- rule_awareness$guessed_block_rule[rule_awareness$Temps_de_mesure == "T1"]
rule_awareness_2 <- rule_awareness$guessed_block_rule[rule_awareness$Temps_de_mesure == "T2"]

round(describe(rule_awareness_1), 2)
round(describe(rule_awareness_2), 2)
```

## Distributional Inspection

To guide the choice of outcome distributions and link functions, the empirical distributions of the questionnaire, eye-tracking, and response-time variables were inspected visually using density plots. As in Study 1, this inspection was used descriptively to verify the bounded nature of the eye-tracking proportions, the approximately symmetric distribution of pre–post difference scores, and the positive skew of the response-time variables.


```{r density_qu_study2, fig.width=8, fig.height=6}
par(mfrow = c(2, 2))

plot(density(na.omit(qu2$Perf_Strivings)), 
     col = "blue", 
     main = "Perfectionistic Strivings", 
     xlab = "ZPS + ZSOP")

plot(density(na.omit(qu2$Perf_Concerns)), 
     col = "red", 
     main = "Perfectionistic Concerns", 
     xlab = "ZCM + ZDA + ZSPP")

plot(density(na.omit(qu2$POS_34)), 
     col = "black", 
     main = "Positive Mood Change", 
     xlab = "")

plot(density(na.omit(qu2$NEG_34)), 
     col = "grey", 
     main = "Negative Mood Change", 
     xlab = "")
```

```{r density_etrt_study2, fig.width=8, fig.height=12}
par(mfrow = c(4, 2))

plot(density(na.omit(et_qu2$first_fix_prob_2)), 
     col='gold', 
     main='Probability of First or Second Fixation (t2)', 
     xlab ='')

plot(density(na.omit(et_qu2$first_fix_latency_2)), 
     col='orange', 
     main='Latency to First Fixation (t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_early_2)), 
     col='purple', 
     main='Dwell Time (Early, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_intermediate_2)),
     col='purple', 
     main='Dwell Time (Intermediate, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_late_2)), 
     col='purple', 
     main='Dwell Time (Late, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_2)), 
     col='purple', main='Dwell Time (t2)', 
     xlab = '')

plot(density(na.omit(rt_qu2$response_time_2)), 
     col='green', 
     main='Response Time (t2)', 
     xlab='')
```


\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# i) Model Inputs and Predictor Coding

## Semantic Coding

The semantic categories of the stimuli were coded using contrast-coded predictors indexing Emotional Valence and Performance Relevance, following the same coding scheme as in Study 1. These codings were used to distinguish valence effects, success-versus-failure effects, and broader performance relevance effects.

For response time, semantic predictors referred to the changed word.

```{r semantic_class_rt_study2}
rt_qu2$Change_category_EV <- 0
rt_qu2$Change_category_EV[rt_qu2$Change_category == "Failure" | rt_qu2$Change_category == "Negative"] <- 1
rt_qu2$Change_category_EV[rt_qu2$Change_category == "Success" | rt_qu2$Change_category == "Positive"] <- -1

rt_qu2$Change_category_PR_SvsF <- 0
rt_qu2$Change_category_PR_SvsF[rt_qu2$Change_category == "Success"] <- -1
rt_qu2$Change_category_PR_SvsF[rt_qu2$Change_category == "Failure"] <- 1

rt_qu2$Change_category_PR_LvsH <- -2
rt_qu2$Change_category_PR_LvsH[rt_qu2$Change_category == "Success"] <- 1
rt_qu2$Change_category_PR_LvsH[rt_qu2$Change_category == "Failure"] <- 1
```

For eye-tracking outcomes, semantic predictors referred to the AOI category.

```{r semantic_class_et_study2}
et_qu2$IA_LABEL_EV <- 0
et_qu2$IA_LABEL_EV[et_qu2$IA_LABEL == "Failure" | et_qu2$IA_LABEL == "Negative"] <- 1
et_qu2$IA_LABEL_EV[et_qu2$IA_LABEL == "Success" | et_qu2$IA_LABEL == "Positive"] <- -1

et_qu2$IA_LABEL_PR_SvsF <- 0
et_qu2$IA_LABEL_PR_SvsF[et_qu2$IA_LABEL == "Success"] <- -1
et_qu2$IA_LABEL_PR_SvsF[et_qu2$IA_LABEL == "Failure"] <- 1

et_qu2$IA_LABEL_PR_LvsH <- -2
et_qu2$IA_LABEL_PR_LvsH[et_qu2$IA_LABEL == "Success"] <- 1
et_qu2$IA_LABEL_PR_LvsH[et_qu2$IA_LABEL == "Failure"] <- 1
```

## ABM Condition

ABM Condition was coded as a three-level factor (Control, Success, Failure), with the control condition as the reference category, consistent with the manuscript specification. 

```{r abm_condition_study2}
qu2$Condition <- relevel(as.factor(qu2$Condition), ref = "Control")
rt_qu2$Condition <- relevel(as.factor(rt_qu2$Condition), ref = "Control")
et_qu2$Condition <- relevel(as.factor(et_qu2$Condition), ref = "Control")
```

## Centering Predictors

Perfectionistic Strivings and Perfectionistic Concerns were mean-centered prior to analysis to reduce multicollinearity.

```{r center_predictors_study2}
qu2$Perf_Strivings_c <- qu2$Perf_Strivings - mean(qu2$Perf_Strivings)
qu2$Perf_Concerns_c  <- qu2$Perf_Concerns  - mean(qu2$Perf_Concerns)

rt_qu2$Perf_Strivings_c <- rt_qu2$Perf_Strivings - mean(rt_qu2$Perf_Strivings)
rt_qu2$Perf_Concerns_c  <- rt_qu2$Perf_Concerns  - mean(rt_qu2$Perf_Concerns)

et_qu2$Perf_Strivings_c <- et_qu2$Perf_Strivings - mean(et_qu2$Perf_Strivings)
et_qu2$Perf_Concerns_c  <- et_qu2$Perf_Concerns  - mean(et_qu2$Perf_Concerns)
```

## Participant and Block Structure

The hierarchical structure of the data (observations nested within participants and blocks) was modeled using penalized smooth terms, following the same approach as in Study 1 (see Appendix A). Participant and block identifiers were converted to numeric format prior to model fitting.

```{r smooth_terms_study2}
rt_qu2$subject_nr_2 <- as.numeric(rt_qu2$subject_nr_2)
rt_qu2$block_loop <- as.numeric(rt_qu2$block_loop)

et_qu2$subject_nr_2 <- as.numeric(et_qu2$subject_nr_2)
et_qu2$block_loop <- as.numeric(et_qu2$block_loop)
```

For eye-tracking analyses, a binary indicator (Change_category01) was created to denote whether a given AOI matched the semantic category targeted by the change rule within a block (0 = non-target, 1 = target).

```{r change_category_study2}
et_qu2$Change_category <- as.factor(et_qu2$Change_category)

et_qu2$Change_category01 <- 0
inds <- which(et_qu2$IA_LABEL == et_qu2$Change_category)
et_qu2$Change_category01[inds] <- 1
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# ii) Task Performance and Control Analysis

This section reports analyses assessing task performance over time and baseline equivalence across ABM conditions.

Given similar group sizes and the robustness of ANOVA to moderate violations of homogeneity of variance, no additional variance homogeneity tests were conducted for these control analyses.

## Task Performance

Paired-samples t-tests were conducted to examine pre–post changes in response accuracy and rule awareness.

```{r task_performance_tests_study2}
# Response accuracy
t.test(accuracy_1, accuracy_2, paired = TRUE)

# Rule awareness
t.test(rule_awareness_1, rule_awareness_2, paired = TRUE)
```

Response accuracy remained stable from T1 to T2, whereas rule awareness increased significantly over time, indicating improved detection of the semantic rule across blocks.

## Group Equivalence

One-way ANOVAs were conducted to assess equivalence across ABM conditions for task performance, perfectionism, and baseline psychological distress.

```{r group_equivalence_study2}
# Tangram performance
fit_Tangrams <- lm(Tangrams ~ Condition, data = qu2)
anova(fit_Tangrams)

# Perfectionism
fit_Strivings <- lm(Perf_Strivings ~ Condition, data = qu2)
anova(fit_Strivings)

fit_Concerns <- lm(Perf_Concerns ~ Condition, data = qu2)
anova(fit_Concerns)

# Baseline distress
fit_Depression <- lm(CESD ~ Condition, data = qu2)
anova(fit_Depression)

fit_Anxiety <- lm(GAD7 ~ Condition, data = qu2)
anova(fit_Anxiety)
```

No differences between ABM conditions were observed for Tangram performance, perfectionistic strivings or concerns, or baseline depressive and anxiety symptoms, indicating successful group equivalence.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# ii) Manipulation Checks: Linear Mixed-Effects Models

To assess whether the attention bias modification (ABM) procedure induced overall changes in attentional allocation independently of perfectionism, **post–pre difference scores** were analysed.

Because these difference scores were approximately symmetric, outcomes were modeled using **Gaussian linear mixed-effects models**.

## Model Overview

- **Outcome:** Difference scores (post – pre attentional indices)  
- **Distribution:** Gaussian  
- **Parameters:**  
  - \(\mu\): mean change in attentional allocation  
  - \(\sigma^2\): residual variance  

## Model Specification

Difference scores were modeled as a function of semantic predictors and ABM condition, with random intercepts for participants and blocks to account for repeated-measures dependencies.

\[
Y_{ij} =
\beta_0
+ \beta_1 EV_{ij}
+ \beta_2 PR_{SvsF,ij}
+ \beta_3 PR_{LvsH,ij}
+ \beta_4 Cond_j
+ \beta_5 (EV_{ij} \times Cond_j)
+ \beta_6 (PR_{SvsF,ij} \times Cond_j)
+ \beta_7 (PR_{LvsH,ij} \times Cond_j)
+ \beta_8 \Delta BR_{ij}
+ u_j + v_i + \epsilon_{ij}
\]

where:

- \(Y_{ij}\): change in attentional allocation for block \(i\) and participant \(j\)  
- \(EV_{ij}\): emotional valence  
- \(PR_{SvsF,ij}\): performance relevance (success vs. failure contrast)  
- \(PR_{LvsH,ij}\): performance relevance (relevant vs. irrelevant contrast)  
- \(Cond_j\): ABM condition (control, success, failure)  
- \(\Delta BR_{ij}\): change in rule awareness  
- \(u_j\): random intercept for participant  
- \(v_i\): random intercept for block  
- \(\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2)\): residual error 

### Fixed Effects

These models test whether attentional allocation changed following the ABM procedure, and whether such changes were **specific to stimulus characteristics** (emotional valence, performance relevance) and **moderated by training condition**.

### Random effects

Random intercepts were included to account for clustering within participants and blocks. In some cases, these effects accounted for negligible variance and resulted in singular fits; they were retained to ensure consistency with the primary modeling framework.

## Early Attentional Measures

**Probability of first or second fixation**

```{r lmm2_first_fix_prob_diff}
lmm2_first_fix_prob_diff <- lmer(
  first_fix_prob_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_first_fix_prob_diff)
```

**Latency to first fixation**

```{r lmm2_first_fix_latency_diff}
lmm2_first_fix_latency_diff <- lmer(
  first_fix_latency_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_first_fix_latency_diff)
```

## Early and Intermediate Dwell Time

**Dwell Time (Early)**

```{r lmm2_dwell_time_early_diff}
lmm2_dwell_time_early_diff <- lmer(
  dwell_time_early_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_dwell_time_early_diff)
```

**Dwell Time (Intermediate)**

```{r lmm2_dwell_time_intermediate_diff}
lmm2_dwell_time_intermediate_diff <- lmer(
  dwell_time_intermediate_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_dwell_time_intermediate_diff)
```


## Late and Trial-Level Dwell Time

**Dwell Time (Late)**

```{r lmm2_dwell_time_late_diff}
lmm2_dwell_time_late_diff <- lmer(
  dwell_time_late_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_dwell_time_late_diff)
```

**Dwell Time (Whole Trial)**

```{r lmm2_dwell_time_diff}
lmm2_dwell_time_diff <- lmer(
  dwell_time_diff ~
    IA_LABEL_EV * Condition + 
    IA_LABEL_PR_LvsH * Condition + 
    IA_LABEL_PR_SvsF * Condition + 
    (1|ID) + (1 + Change_category01|block_loop),
  data = et_qu2
) 
summary(lmm2_dwell_time_diff)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Path *a'*: Moderating effect of ABM on Perfectionism → Attention Bias

Post-ABM attentional measures (probability of first or second fixation, latency to first fixation, dwell time, and response time) were analyzed using **GAMLSS**, following the modelling framework described in Study 1 (see Appendix A).

## Hierarchical Model-Building Strategy

Models were estimated hierarchically:

- **Baseline model:** Included pre-ABM attentional values and control terms (smooth terms and dispersion predictors)  

- **Partial model:** Added ABM condition and the **perfectionism × semantic contrast** interaction identified in Study 1  

- **Full model:** Added the **three-way interaction** between ABM condition, perfectionism, and semantic contrast  

Perfectionistic Strivings and Perfectionistic Concerns were examined in separate models.

## Model Diagnostic Functions

Model fit was evaluated using residual-versus-fitted plots and simulation-based predictive checks comparing observed and model-implied outcome distributions.

```{r model_diagnostics_functions, echo=FALSE}
# Residuals vs fitted plot
diag_resid_fitted <- function(model) {
  ggplot(
    data.frame(
      fitted = predict(model),
      residuals = resid(model)
    ),
    aes(x = fitted, y = residuals)
  ) +
    geom_point(alpha = 0.5) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    ggtitle(paste("Residuals vs. Fitted Values:", deparse(substitute(model)))) +
    theme_minimal()
}

# Posterior predictive check for beta GAMLSS
diag_ppc_beta <- function(model) {
  mu_hat <- fitted(model, "mu")
  sigma_hat <- fitted(model, "sigma")
  
  phi_hat <- (1 / sigma_hat^2) - 1
  
  set.seed(123)
  predicted_values <- rbeta(
    length(mu_hat),
    shape1 = mu_hat * phi_hat,
    shape2 = (1 - mu_hat) * phi_hat
  )
  
  observed_values <- model$y
  
  ggplot() +
    geom_density(aes(x = observed_values, color = "Observed"), linetype = "dashed", linewidth = 1) +
    geom_density(aes(x = predicted_values, color = "Predicted"), linewidth = 1) +
    labs(
      title = paste("Observed vs. Predicted Values:", deparse(substitute(model))),
      x = "Value",
      y = "Probability Density"
    ) +
    scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
    theme_minimal()
}

# Posterior predictive check for gamma GAMLSS
diag_ppc_gamma <- function(model) {
  mu_hat <- fitted(model, "mu")
  sigma_hat <- fitted(model, "sigma")
  
  alpha_hat <- 1 / (sigma_hat^2)
  beta_hat  <- mu_hat / alpha_hat
  
  set.seed(123)
  predicted_values <- rgamma(length(mu_hat), shape = alpha_hat, scale = beta_hat)
  
  observed_values <- model$y
  
  ggplot() +
    geom_density(aes(x = observed_values, color = "Observed"), linetype = "dashed", linewidth = 1) +
    geom_density(aes(x = predicted_values, color = "Predicted"), linewidth = 1) +
    labs(
      title = paste("Observed vs. Predicted Values:", deparse(substitute(model))),
      x = "Value",
      y = "Probability Density"
    ) +
    scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
    theme_minimal()
}
```


## iii) Beta Regression for Eye-Tracking Indices

As in Study 1, eye-tracking indices represent continuous proportions bounded between 0 and 1 and were therefore modeled using the **beta distribution**.

### Model Overview

- **Outcome:** Post-ABM attentional indices (modeled as proportions)  
- **Distribution:** Beta  
- **Parameters:**  
  - \(\mu\): mean (expected proportion)  
  - \(\sigma\): dispersion (variability around the mean)  

The link function for the mean parameter (\(\mu\)) was selected based on the empirical distribution of each outcome (logit or cauchit), as in Study 1.

---

### Model Specification

Models included semantic predictors, ABM condition, and perfectionism, as well as their interactions. To reduce model complexity and focus on theoretically relevant effects, **only the semantic contrasts that significantly interacted with perfectionism in Study 1 were retained**.

To account for baseline differences in attentional allocation, the corresponding **pre-ABM measure** was included as a covariate in all models.

#### Mean Submodel (\(\mu\))

\[
g(\mu_{ij}) =
\beta_0
+ \beta_1 PreAB_{ij}
+ \beta_2 SC_{ij}
+ \beta_3 Perf_j
+ \beta_4 Cond_j
+ \beta_5 (SC_{ij} \times Perf_j)
+ \beta_6 (SC_{ij} \times Cond_j)
+ \beta_7 (Perf_j \times Cond_j)
+ \beta_8 (SC_{ij} \times Perf_j \times Cond_j)
+ f_1(\text{subject}_j)
+ f_2(\text{block}_i)
+ f_3(\text{ChangeCategory}_{ij}, \text{by block}_i)
\]

where:

- \(g(\cdot)\): link function (logit or cauchit)  
- \(\mu_{ij}\): expected attentional allocation for block \(i\) and participant \(j\)  
- \(PreAB_{ij}\): pre-ABM attentional measure (baseline covariate)  
- \(SC_{ij}\): retained semantic contrast (from Study 1; e.g., Emotional Valence or Performance Relevance)  
- \(Perf_j\): perfectionism (Perfectionistic Strivings or Concerns; modeled separately, mean-centered)  
- \(Cond_j\): ABM condition (control, success, failure)  
- \(f_1, f_2, f_3\): penalized smooth terms for participant, block, and block-varying Change Category effects  

---

#### Dispersion Submodel (\(\sigma\))

\[
\text{logit}(\sigma_{ij}) =
\gamma_0
+ \gamma_1 BR_{ij}
+ \gamma_2 Cond_j
\]

where:

- \(\sigma_{ij}\): dispersion (variability in attentional allocation)  
- \(BR_{ij}\): rule awareness (0 = no, 1 = yes)  
- \(Cond_j\): ABM condition  

---

ABM condition was additionally included to account for potential
condition-dependent differences in the variability of attentional
allocation, beyond effects on the mean.


### Data Preparation for Beta Models

To reduce memory usage and computation time, a subset containing only variables required for model fitting was created.

```{r subset_et_data_study2}
sub_et_qu2 <- et_qu2[c("subject_nr_1", "first_fix_prob_1", "first_fix_latency_1", "dwell_time_1",
                       "dwell_time_early_1", "dwell_time_intermediate_1", "dwell_time_late_1",
                       "guessed_block_rule_1",
                       "subject_nr_2", "first_fix_prob_2", "first_fix_latency_2", "dwell_time_2",
                       "dwell_time_early_2", "dwell_time_intermediate_2", "dwell_time_late_2",
                       "guessed_block_rule_2",
                       "block_loop", "IA_LABEL_PR_SvsF", "IA_LABEL_PR_LvsH", "IA_LABEL_EV", 
                       "Change_category01", "Condition",
                       "Perf_Strivings_c", "Perf_Concerns_c")]
```

Because the beta distribution is defined on the open interval $(0, 1)$, observations equal to 0 or 1 were slightly adjusted prior to model fitting.

```{r transform01_et_study2}
transform01 <- function(x) {
  (x * (length(x) - 1) + 0.5) / (length(x))
}

sub_et_qu2$first_fix_prob_1_t01 <- transform01(sub_et_qu2$first_fix_prob_1)
sub_et_qu2$first_fix_prob_2_t01 <- transform01(sub_et_qu2$first_fix_prob_2)

sub_et_qu2$dwell_time_early_1_t01 <- transform01(sub_et_qu2$dwell_time_early_1)
sub_et_qu2$dwell_time_early_2_t01 <- transform01(sub_et_qu2$dwell_time_early_2)

sub_et_qu2$dwell_time_intermediate_1_t01 <- transform01(sub_et_qu2$dwell_time_intermediate_1)
sub_et_qu2$dwell_time_intermediate_2_t01 <- transform01(sub_et_qu2$dwell_time_intermediate_2)

sub_et_qu2$dwell_time_late_1_t01 <- transform01(sub_et_qu2$dwell_time_late_1)
sub_et_qu2$dwell_time_late_2_t01 <- transform01(sub_et_qu2$dwell_time_late_2)
```

A custom inverse cauchit function was defined to back-transform predictions from the link scale to the proportion scale.

```{r inv.cauchit_function_study2}
inv.cauchit <- function(eta) {
  (1 / pi) * atan(eta) + 0.5
}
```

### 1. Probability of First or Second Fixation

Probability of first or second fixation was modeled using a **beta GAMLSS** with a logit link for the mean parameter.

##### bm0_first_fix_prob_2

**Baseline model**

```{r bm0_first_fix_prob_2_study2}
bm0_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  family = BE(mu.link = "logit"),
  sigma.formula = ~ guessed_block_rule_2,
  data = na.omit(sub_et_qu2)
)
summary(bm0_first_fix_prob_2)
```

**Back-transformed coefficients (bm0)**

```{r bm0_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm0_first_fix_prob_2$mu.coefficients),4))
```

##### bm1.1_first_fix_prob_2

**Partial model: Perfectionistic Strivings**

Following Study 1, the partial model for Perfectionistic Strivings included Emotional Valence, ABM condition, and the Emotional Valence × Perfectionistic Strivings interaction.

```{r bm1.1_first_fix_prob_2_study2}
bm1.1_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    Condition +
    IA_LABEL_EV * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.1_first_fix_prob_2)
```

**Back-transformed coefficients (bm1.1)**

```{r bm1.1_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm1.1_first_fix_prob_2$mu.coefficients), 4))
```

**Comparison of model fit (bm1.1 vs. bm0)**

```{r bm1.1_first_fix_prob_2_fit_study2}
lrtest(bm0_first_fix_prob_2, bm1.1_first_fix_prob_2)

AIC(bm1.1_first_fix_prob_2, bm0_first_fix_prob_2)
```


##### bm1.2_first_fix_prob_2

**Partial model: Perfectionistic Concerns**

Following Study 1, the partial model for Perfectionistic Concerns included Performance Relevance (success vs. failure), ABM condition, and the Performance Relevance × Perfectionistic Concerns interaction.

```{r bm1.2_first_fix_prob_2_study2}
bm1.2_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    Condition +
    IA_LABEL_PR_SvsF * Perf_Concerns_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.2_first_fix_prob_2)
```

**Back-transformed coefficients (bm1.2)**

```{r bm1.2_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm1.2_first_fix_prob_2$mu.coefficients), 4))
```

**Comparison of model fit (bm1.2 vs. bm0)**

```{r bm1.2_first_fix_prob_2_fit_study2}
lrtest(bm0_first_fix_prob_2, bm1.2_first_fix_prob_2)

AIC(bm1.2_first_fix_prob_2, bm0_first_fix_prob_2)
```

##### bm2.1_first_fix_prob_2

**Full model: Perfectionistic Strivings**

The full model for Perfectionistic Strivings added the three-way interaction between Emotional Valence, ABM condition, and Perfectionistic Strivings.

```{r bm2.1_first_fix_prob_2_study2}
bm2.1_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    IA_LABEL_EV * Condition * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1_first_fix_prob_2)
```

**Back-transformed coefficients (bm2.1)**

```{r bm2.1_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm2.1_first_fix_prob_2$mu.coefficients), 4))
```

**Comparison of model fit (bm2.1 vs. bm1.1)**

```{r bm2.1_first_fix_prob_2_fit_study2}
lrtest(bm1.1_first_fix_prob_2, bm2.1_first_fix_prob_2)

AIC(bm1.1_first_fix_prob_2, bm2.1_first_fix_prob_2)
```

**Model diagnostics (bm2.1)**

```{r bm2.1_first_fix_prob_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.1_first_fix_prob_2)
p2 <- diag_ppc_beta(bm2.1_first_fix_prob_2)

grid.arrange(p1, p2, ncol = 2)
```


**Decomposition of the interaction between Perfectionistic Strivings, Emotional Valence, and ABM Condition**

To interpret the three-way interaction, the model was reparameterized so that the perfectionism effect could be estimated separately within specific ABM conditions.

###### bm2.1a_first_fix_prob_2

**ABM Condition = Failure**

```{r bm2.1a_first_fix_prob_2_study2}
sub_et_qu2$Condition_F <- relevel(sub_et_qu2$Condition, ref = "Failure")

bm2.1a_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    IA_LABEL_EV * Condition_F * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_F,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1a_first_fix_prob_2)
```

**Back-transformed coefficients (bm2.1a)**

```{r bm2.1a_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm2.1a_first_fix_prob_2$mu.coefficients),4))
```


###### bm2.1b_first_fix_prob_2

**ABM Condition = Success**

```{r bm2.1b_first_fix_prob_2_study2}
sub_et_qu2$Condition_S <- relevel(sub_et_qu2$Condition, ref = "Success")

bm2.1b_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    IA_LABEL_EV * Condition_S * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_S,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1b_first_fix_prob_2)
```

**Back-transformed coefficients (bm2.1b)**

```{r bm2.1b_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm2.1b_first_fix_prob_2$mu.coefficients),4))
```

##### bm2.2_first_fix_prob_2

**Full model: Perfectionistic Concerns**

The full model for Perfectionistic Concerns added the three-way interaction between Performance Relevance (success vs. failure), ABM condition, and Perfectionistic Concerns.

```{r bm2.2_first_fix_prob_2_study2}
bm2.2_first_fix_prob_2 <- gamlss(
  first_fix_prob_2_t01 ~ 
    first_fix_prob_1 +
    IA_LABEL_PR_SvsF * Condition * Perf_Concerns_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2_first_fix_prob_2)
```

**Back-transformed coefficients (bm2.2)**

```{r bm2.2_first_fix_prob_2_coef_study2}
print(round(inv.logit(bm2.2_first_fix_prob_2$mu.coefficients),4))
```

**Comparison of model fit (bm2.2 vs. bm1.2)**

```{r bm2.2_first_fix_prob_2_fit_study2}
lrtest(bm1.2_first_fix_prob_2, bm2.2_first_fix_prob_2)

AIC(bm1.2_first_fix_prob_2, bm2.2_first_fix_prob_2)
```

**Model diagnostics (bm2.2)**

```{r bm2.2_first_fix_prob_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.2_first_fix_prob_2)
p2 <- diag_ppc_beta(bm2.2_first_fix_prob_2)

grid.arrange(p1, p2, ncol = 2)
```

**Plotting the retained interaction**

The final plot focuses on the retained three-way interaction between Perfectionistic Strivings, Emotional Valence, and ABM condition.

```{r bm2_first_fix_prob_2_plot_study2, fig.width=12, fig.height=4}
preds_first_fix_prob_EV_PS <- ggpredict(
  bm2.1_first_fix_prob_2,
  terms = c("Perf_Strivings_c", "IA_LABEL_EV", "Condition")
)

ffp_EV_PS <- ggplot(preds_first_fix_prob_EV_PS, aes(x = x, y = predicted, color = group, linetype = facet)) +
  geom_line(size = 1) +
  scale_color_manual(
    values = c("-1" = "purple", "0" = "lightgreen", "1" = "skyblue"),
    labels = c("Positive", "Neutral", "Negative")
  ) +
  facet_wrap(~facet, labeller = labeller(facet = c("Control" = "Control", "Success" = "Success", "Failure" = "Failure"))) +
  scale_linetype_manual(
    name = "Condition",
    values = c("Control" = "dashed", "Success" = "dashed", "Failure" = "solid"),
    labels = c("Control", "Success", "Failure")
  ) +
  labs(
    x = "Perfectionistic Strivings",
    y = "",
    color = "Emotional Valence"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

grid.arrange(
  ffp_EV_PS,
  ncol = 1, nrow = 1,
  top = textGrob("Predicted First Fixation Probability (t2)",
                 gp = gpar(fontsize = 16, fontface = "bold"))
)
```
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

## 2 Latency to First Fixation

No models were fitted, as no effects of perfectionism were observed in Study 1.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

## 3. Dwell Time (Early Phase)

Early-phase dwell time was modeled using a **beta GAMLSS** with a logit link for the mean parameter.

##### bm0_dwell_time_early_2

**Baseline model**

```{r bm0_dwell_time_early_2_study2}
bm0_dwell_time_early_2 <- gamlss(
  dwell_time_early_2_t01 ~ 
    dwell_time_early_1 +
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm0_dwell_time_early_2)
```

**Back-transformed coefficients (bm0)**

```{r bm0_dwell_time_early_2_coef_study2}
print(round(inv.logit(bm0_dwell_time_early_2$mu.coefficients),4))
```


##### bm1.1_dwell_time_early_2

**Partial model: Perfectionistic Strivings**

Following Study 1, the partial model for Perfectionistic Strivings included Emotional Valence, ABM condition, and the Emotional Valence × Perfectionistic Strivings interaction.

```{r bm1.1_dwell_time_early_2_study2}
bm1.1_dwell_time_early_2 <- gamlss(
  dwell_time_early_2_t01 ~ 
    dwell_time_early_1 +
    Condition +
    IA_LABEL_EV * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.1_dwell_time_early_2)
```

**Back-transformed coefficients (bm1.1)**

```{r bm1.1_dwell_time_early_2_coef_study2}
print(round(inv.logit(bm1.1_dwell_time_early_2$mu.coefficients), 4))
```

**Comparison of model fit (bm1.1 vs. bm0)**

```{r bm1.1_dwell_time_early_2_fit_study2}
lrtest(bm0_dwell_time_early_2, bm1.1_dwell_time_early_2)

AIC(bm1.1_dwell_time_early_2, bm0_dwell_time_early_2)
```


##### bm1.2_dwell_time_early_2

**Partial model: Perfectionistic Concerns**

Following Study 1, the partial model for Perfectionistic Concerns included Performance Relevance (relevant vs. irrelevant), ABM condition, and the Performance Relevance × Perfectionistic Concerns interaction.

```{r bm1.2_dwell_time_early_2_study2}
bm1.2_dwell_time_early_2 <- gamlss(
  dwell_time_early_2_t01 ~ 
    dwell_time_early_1 +
    Condition +
    IA_LABEL_PR_LvsH * Perf_Concerns_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.2_dwell_time_early_2)
```

**Back-transformed coefficients (bm1.2)**

```{r bm1.2_dwell_time_early_2_coef_study2}
print(round(inv.logit(bm1.2_dwell_time_early_2$mu.coefficients), 4))
```

**Comparison of model fit (bm1.2 vs. bm0)**

```{r bm1.2_dwell_time_early_2_fit_study2}
lrtest(bm0_dwell_time_early_2, bm1.2_dwell_time_early_2)

AIC(bm1.2_dwell_time_early_2, bm0_dwell_time_early_2)
```

##### bm2.1_dwell_time_early_2

**Full model: Perfectionistic Strivings**

The full model for Perfectionistic Strivings added the three-way interaction between Emotional Valence, ABM condition, and Perfectionistic Strivings.

```{r bm2.1_dwell_time_early_2_study2}
bm2.1_dwell_time_early_2 <- gamlss(
  dwell_time_early_2_t01 ~ 
    dwell_time_early_1 +
    IA_LABEL_EV * Perf_Strivings_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1_dwell_time_early_2)
```

**Back-transformed coefficients (bm2.1)**

```{r bm2.1_dwell_time_early_2_coef_study2}
print(round(inv.logit(bm2.1_dwell_time_early_2$mu.coefficients), 4))
```

**Comparison of model fit (bm2.1 vs. bm1.1)**

```{r bm2.1_dwell_time_early_2_fit_study2}
lrtest(bm1.1_dwell_time_early_2, bm2.1_dwell_time_early_2)

AIC(bm1.1_dwell_time_early_2, bm2.1_dwell_time_early_2)
```

**Model diagnostics (bm2.1)**

```{r bm2.1_dwell_time_early_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.1_dwell_time_early_2)
p2 <- diag_ppc_beta(bm2.1_dwell_time_early_2)

grid.arrange(p1, p2, ncol = 2)
```


##### bm2.2_dwell_time_early_2

**Full model: Perfectionistic Concerns**

The full model for Perfectionistic Concerns added the three-way interaction between Performance Relevance (relevant vs. irrelevant), ABM condition, and Perfectionistic Concerns.

```{r bm2.2_dwell_time_early_2_study2}
bm2.2_dwell_time_early_2 <- gamlss(
  dwell_time_early_2_t01 ~ 
    dwell_time_early_1 +
    IA_LABEL_PR_LvsH * Perf_Concerns_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2_dwell_time_early_2)
```

**Back-transformed coefficients (bm2.2)**

```{r bm2.2_dwell_time_early_2_coef_study2}
print(round(inv.logit(bm2.2_dwell_time_early_2$mu.coefficients), 4))
```

**Comparison of model fit (bm2.2 vs. bm1.2)**

```{r bm2.2_dwell_time_early_2_fit_study2}
lrtest(bm1.2_dwell_time_early_2, bm2.2_dwell_time_early_2)

AIC(bm1.2_dwell_time_early_2, bm2.2_dwell_time_early_2)
```

**Model diagnostics (bm2.2)**

```{r bm2.2_dwell_time_early_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.2_dwell_time_early_2)
p2 <- diag_ppc_beta(bm2.2_dwell_time_early_2)

grid.arrange(p1, p2, ncol = 2)
```
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

### 4. Dwell Time (Intermediate Phase)

Intermediate-phase dwell time was modeled using a **beta GAMLSS** with a logit link for the mean parameter.

##### bm0_dwell_time_intermediate_2

**Baseline model**

```{r bm0_dwell_time_intermediate_2_study2}
bm0_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm0_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm0)**

```{r bm0_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm0_dwell_time_intermediate_2$mu.coefficients), 4))
```


##### bm1.1_dwell_time_intermediate_2

**Partial model: Perfectionistic Strivings**

Following Study 1, the partial model for Perfectionistic Strivings included Emotional Valence, ABM condition, and the Emotional Valence × Perfectionistic Strivings interaction.

```{r bm1.1_dwell_time_intermediate_2_study2}
bm1.1_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    Condition +
    IA_LABEL_EV * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.1_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm1.1)**

```{r bm1.1_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm1.1_dwell_time_intermediate_2$mu.coefficients),4))
```

**Comparison of model fit (bm1.1 vs. bm0)**

```{r bm1.1_dwell_time_intermediate_2_fit_study2}
lrtest(bm0_dwell_time_intermediate_2, bm1.1_dwell_time_intermediate_2)

AIC(bm1.1_dwell_time_intermediate_2, bm0_dwell_time_intermediate_2)
```

##### bm1.2_dwell_time_intermediate_2

**Partial model: Perfectionistic Concerns**

Following Study 1, the partial model for Perfectionistic Concerns included Performance Relevance (relevant vs. irrelevant), ABM condition, and the Performance Relevance × Perfectionistic Concerns interaction.

```{r bm1.2_dwell_time_intermediate_2_study2}
bm1.2_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    Condition +
    IA_LABEL_PR_LvsH * Perf_Concerns_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.2_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm1.2)**

```{r bm1.2_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm1.2_dwell_time_intermediate_2$mu.coefficients),4))
```

**Comparison of model fit (bm1.2 vs. bm0)**

```{r bm1.2_dwell_time_intermediate_2_fit_study2}
lrtest(bm0_dwell_time_intermediate_2, bm1.2_dwell_time_intermediate_2)

AIC(bm1.2_dwell_time_intermediate_2, bm0_dwell_time_intermediate_2)
```


##### bm2.1_dwell_time_intermediate_2

**Full model: Perfectionistic Strivings**

The full model for Perfectionistic Strivings added the three-way interaction between Emotional Valence, ABM condition, and Perfectionistic Strivings.

```{r bm2.1_dwell_time_intermediate_2_study2}
bm2.1_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    IA_LABEL_EV * Perf_Strivings_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm2.1)**

```{r bm2.1_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm2.1_dwell_time_intermediate_2$mu.coefficients),4))
```

**Comparison of model fit (bm2.1 vs. bm1.1)**

```{r bm2.1_dwell_time_intermediate_2_fit_study2}
lrtest(bm1.1_dwell_time_intermediate_2, bm2.1_dwell_time_intermediate_2)

AIC(bm1.1_dwell_time_intermediate_2, bm2.1_dwell_time_intermediate_2)
```

**Model diagnostics (bm2.1)**

```{r bm2.1_dwell_time_intermediate_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.1_dwell_time_intermediate_2)
p2 <- diag_ppc_beta(bm2.1_dwell_time_intermediate_2)

grid.arrange(p1, p2, ncol = 2)
```

##### bm2.2_dwell_time_intermediate_2

**Full model: Perfectionistic Concerns**

The full model for Perfectionistic Concerns added the three-way interaction between Performance Relevance (relevant vs. irrelevant), ABM condition, and Perfectionistic Concerns.

```{r bm2.2_dwell_time_intermediate_2_study2}
bm2.2_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    IA_LABEL_PR_LvsH * Perf_Concerns_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm2.2)**

```{r bm2.2_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm2.2_dwell_time_intermediate_2$mu.coefficients),4))
```

**Comparison of model fit (bm2.2 vs. bm1.2)**

```{r bm2.2_dwell_time_intermediate_2_fit_study2}
lrtest(bm1.2_dwell_time_intermediate_2, bm2.2_dwell_time_intermediate_2)

AIC(bm1.2_dwell_time_intermediate_2, bm2.2_dwell_time_intermediate_2)
```

**Model diagnostics (bm2.2)**

```{r bm2.2_dwell_time_intermediate_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.2_dwell_time_intermediate_2)
p2 <- diag_ppc_beta(bm2.2_dwell_time_intermediate_2)

grid.arrange(p1, p2, ncol = 2)
```

**Decomposition of the interaction between Perfectionistic Concerns, Performance Relevance, and ABM condition**

###### bm2.2a_dwell_time_intermediate_2

**ABM Condition = Failure**

```{r bm2.2a_dwell_time_intermediate_2_study2}
sub_et_qu2$Condition_F <- relevel(sub_et_qu2$Condition, ref = "Failure")

bm2.2a_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    IA_LABEL_PR_LvsH * Perf_Concerns_c * Condition_F + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_F,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2a_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm2.2a)**

```{r bm2.2a_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm2.2a_dwell_time_intermediate_2$mu.coefficients),4))
```


###### bm2.2b_dwell_time_intermediate_2

**ABM Condition = Success**

```{r bm2.2b_dwell_time_intermediate_2_study2}
sub_et_qu2$Condition_S <- relevel(sub_et_qu2$Condition, ref = "Success")

bm2.2b_dwell_time_intermediate_2 <- gamlss(
  dwell_time_intermediate_2_t01 ~ 
    dwell_time_intermediate_1 +
    IA_LABEL_PR_LvsH * Perf_Concerns_c * Condition_S + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_S,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2b_dwell_time_intermediate_2)
```

**Back-transformed coefficients (bm2.2b)**

```{r bm2.2b_dwell_time_intermediate_2_coef_study2}
print(round(inv.logit(bm2.2b_dwell_time_intermediate_2$mu.coefficients),4))
```

**Plotting the retained interaction**

```{r bm2.2_dwell_time_intermediate_2_plot_study2, fig.width = 12, fig.height=4}
preds_dwell_time_intermediate_PC <- ggpredict(
  bm2.2_dwell_time_intermediate_2,
  terms = c("Perf_Concerns_c", "IA_LABEL_PR_LvsH", "Condition")
)

dti_PC <- ggplot(preds_dwell_time_intermediate_PC, aes(x = x, y = predicted, color = group, linetype = facet)) +
  geom_line(size = 1) +
  scale_color_manual(
    values = c("-2" = "grey", "1" = "gold"),
    labels = c("Irrelevant", "Relevant")
  ) +
  facet_wrap(
    ~facet,
    labeller = labeller(facet = c("Control" = "Control", "Success" = "Success", "Failure" = "Failure"))
  ) +
  scale_linetype_manual(
    name = "Condition",
    values = c("Control" = "solid", "Success" = "dashed", "Failure" = "dashed"),
    labels = c("Control", "Success", "Failure")
  ) +
  labs(
    x = "Perfectionistic Concerns",
    y = "",
    color = "Performance Relevance"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

grid.arrange(
  dti_PC,
  ncol = 1, nrow = 1,
  top = textGrob("Predicted Dwell Time (Intermediate, t2)",
                 gp = gpar(fontsize = 16, fontface = "bold"))
)
```
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

### 5. Dwell Time (Late Phase)

Late-phase dwell time was modeled using a **beta GAMLSS** with a logit link for the mean parameter.

##### bm0_dwell_time_late_2

**Baseline model**

```{r bm0_dwell_time_late_2_study2}
bm0_dwell_time_late_2 <- gamlss(
  dwell_time_late_2_t01 ~ 
    dwell_time_late_1 +
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm0_dwell_time_late_2)
```

**Back-transformed coefficients (bm0)**

```{r bm0_dwell_time_late_2_coef_study2}
print(round(inv.logit(bm0_dwell_time_late_2$mu.coefficients),4))
```


##### bm1.1_dwell_time_late_2

**Partial model: Perfectionistic Strivings**

Following Study 1, the partial model for Perfectionistic Strivings included Performance Relevance (relevant vs. irrelevant), ABM condition, and the Performance Relevance × Perfectionistic Strivings interaction.

```{r bm1.1_dwell_time_late_2_study2}
bm1.1_dwell_time_late_2 <- gamlss(
  dwell_time_late_2_t01 ~ 
    dwell_time_late_1 +
    Condition +
    IA_LABEL_PR_LvsH * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.1_dwell_time_late_2)
```

**Back-transformed coefficients (bm1.1)**

```{r bm1.1_dwell_time_late_2_coef_study2}
print(round(inv.logit(bm1.1_dwell_time_late_2$mu.coefficients),4))
```

**Comparison of model fit (bm1.1 vs. bm0)**

```{r bm1.1_dwell_time_late_2_fit_study2}
lrtest(bm0_dwell_time_late_2, bm1.1_dwell_time_late_2)

AIC(bm0_dwell_time_late_2, bm1.1_dwell_time_late_2)
```


##### bm2.1_dwell_time_late_2

**Full model: Perfectionistic Strivings**

The full model for Perfectionistic Strivings added the three-way interaction between Performance Relevance, ABM condition, and Perfectionistic Strivings.

```{r bm2.1_dwell_time_late_2_study2}
bm2.1_dwell_time_late_2 <- gamlss(
  dwell_time_late_2_t01 ~ 
    dwell_time_late_1 +
    IA_LABEL_PR_LvsH * Condition * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "logit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.1_dwell_time_late_2)
```

**Back-transformed coefficients (bm2.1)**

```{r bm2.1_dwell_time_late_2_coef_study2}
print(round(inv.logit(bm2.1_dwell_time_late_2$mu.coefficients),4))
```

**Comparison of model fit (bm2.1 vs. bm1.1)**

```{r bm2.1_dwell_time_late_2_fit_study2}
lrtest(bm1.1_dwell_time_late_2, bm2.1_dwell_time_late_2)

AIC(bm1.1_dwell_time_late_2, bm2.1_dwell_time_late_2)
```

**Model diagnostics (bm2.1)**

```{r bm2.1_dwell_time_late_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.1_dwell_time_late_2)
p2 <- diag_ppc_beta(bm2.1_dwell_time_late_2)

grid.arrange(p1, p2, ncol = 2)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

### 6. Dwell Time (Whole Trial)

Whole-trial dwell time was modeled using a **beta GAMLSS** with a **cauchit** link for the mean parameter, as in Study 1. The cauchit link was retained because the empirical distribution of whole-trial dwell time showed heavier tails than the phase-specific dwell time indices.

##### bm0_dwell_time_2

**Baseline model**

```{r bm0_dwell_time_2_study2}
bm0_dwell_time_2 <- gamlss(
  dwell_time_2 ~ 
    dwell_time_1 +
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "cauchit"),
  data = na.omit(sub_et_qu2)
)
summary(bm0_dwell_time_2)
```

**Back-transformed coefficients (bm0)**

```{r bm0_dwell_time_2_coef_study2}
print(round(inv.cauchit(bm0_dwell_time_2$mu.coefficients),4))
```


##### bm1.2_dwell_time_2

**Partial model: Perfectionistic Concerns**

Following Study 1, the partial model for whole-trial dwell time retained Emotional Valence, ABM condition, and the Emotional Valence × Perfectionistic Concerns interaction.

```{r bm1.2_dwell_time_2_study2}
bm1.2_dwell_time_2 <- gamlss(
  dwell_time_2 ~ 
    dwell_time_1 +
    Condition + 
    IA_LABEL_EV * Perf_Concerns_c + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "cauchit"),
  data = na.omit(sub_et_qu2)
)
summary(bm1.2_dwell_time_2)
```

**Back-transformed coefficients (bm1.2)**

```{r bm1.2_dwell_time_2_coef_study2}
print(round(inv.cauchit(bm1.2_dwell_time_2$mu.coefficients),4))
```

**Comparison of model fit (bm1.2 vs. bm0)**

```{r bm1.2_dwell_time_2_fit_study2}
lrtest(bm0_dwell_time_2, bm1.2_dwell_time_2)

AIC(bm0_dwell_time_2, bm1.2_dwell_time_2)
```

##### bm2_dwell_time_2

**Full model: Perfectionistic Concerns**

The full model added the three-way interaction between Emotional Valence, ABM condition, and Perfectionistic Concerns.

```{r bm2.2_dwell_time_2_study2}
bm2.2_dwell_time_2 <- gamlss(
  dwell_time_2 ~ 
    dwell_time_1 +
    IA_LABEL_EV * Perf_Concerns_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  family = BE(mu.link = "cauchit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2_dwell_time_2)
```

**Back-transformed coefficients (bm2.2)**

```{r bm2.2_dwell_time_2_coef_study2}
print(round(inv.cauchit(bm2.2_dwell_time_2$mu.coefficients),4))
```

**Comparison of model fit (bm2.2 vs. bm1.2)**

```{r bm2_dwell_time_2_fit_study2}
lrtest(bm1.2_dwell_time_2, bm2.2_dwell_time_2)

AIC(bm1.2_dwell_time_2, bm2.2_dwell_time_2)
```

**Model diagnostics (bm2.2)**

```{r bm2.2_dwell_time_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(bm2.2_dwell_time_2)
p2 <- diag_ppc_beta(bm2.2_dwell_time_2)

grid.arrange(p1, p2, ncol = 2)
```

**Decomposition of the interaction between Emotional Valence, Perfectionistic Concerns, and ABM Condition**

###### bm2.2a_dwell_time_2 

**ABM Condition = Failure**

```{r bm2.2a_dwell_time_2_study2}
sub_et_qu2$Condition_F <- relevel(sub_et_qu2$Condition, ref = "Failure")

bm2.2a_dwell_time_2 <- gamlss(
  dwell_time_2 ~ 
    dwell_time_1 +
    IA_LABEL_EV * Perf_Concerns_c * Condition_F + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_F,
  family = BE(mu.link = "cauchit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2a_dwell_time_2)
```

**Back-transformed coefficients (bm2.2a)**

```{r bm2a_dwell_time_2_coef_study2}
print(round(inv.cauchit(bm2.2a_dwell_time_2$mu.coefficients), 4))
```

###### bm2.2b_dwell_time_2

**ABM Condition = Success**

```{r bm2.2b_dwell_time_2_study2}
sub_et_qu2$Condition_S <- relevel(sub_et_qu2$Condition, ref = "Success")

bm2.2b_dwell_time_2 <- gamlss(
  dwell_time_2 ~ 
    dwell_time_1 +
    IA_LABEL_EV * Perf_Concerns_c * Condition_S + 
    pb(subject_nr_2) + 
    pb(block_loop) + 
    pb(Change_category01, by = block_loop),
  sigma.formula = ~ guessed_block_rule_2 + Condition_S,
  family = BE(mu.link = "cauchit"),
  data = na.omit(sub_et_qu2)
)
summary(bm2.2b_dwell_time_2)
```

**Back-transformed coefficients (bm2b)**

```{r bm2.2b_dwell_time_2_coef_study2}
print(round(inv.cauchit(bm2.2b_dwell_time_2$mu.coefficients),4))
```

**Plotting the retained interaction**

```{r bm2.2_dwell_time_2_plot_study2, fig.width=12, fig.height=4}
preds_dwell_time_PC <- ggpredict(bm2.2_dwell_time_2, terms = c("Perf_Concerns_c", "IA_LABEL_EV", "Condition"))

dtw_PC <- ggplot(preds_dwell_time_PC, aes(x = x, y = predicted, color = group, linetype = facet)) +
  geom_line(size = 1) +
  scale_color_manual(
    values = c("-1" = "purple", "0" = "lightgreen", "1" = "skyblue"),
    labels = c("Positive", "Neutral", "Negative")
  ) +
  facet_wrap(~facet, labeller = labeller(facet = c("Control" = "Control", "Success" = "Success", "Failure" = "Failure"))) +
  scale_linetype_manual(
    name = "Condition",
    values = c("Control" = "solid", "Success" = "dashed", "Failure" = "dashed"),
    labels = c("Control", "Success", "Failure")
  ) +
  labs(
    x = "Perfectionistic Concerns",
    y = "",
    color = "Emotional Valence"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

grid.arrange(
  dtw_PC,
  ncol = 1, nrow = 1,
  top = textGrob("Predicted Dwell Time (Whole Trial, t2)",
                 gp = gpar(fontsize = 16, fontface = "bold"))
)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

## iv) Gamma Regression for Response Time

Post-ABM response times were analyzed using **gamma regression within the GAMLSS framework**, following the approach described in Study 1 (see Appendix A). Response times are continuous, strictly positive, and right-skewed, making the **gamma distribution** appropriate.

A **log link** was used to ensure positive predictions and to allow coefficients to be interpreted on a multiplicative scale.

### Model Overview

- **Outcome:** Post-ABM response time  
- **Distribution:** Gamma  
- **Link function:** Log  
- **Parameters:**  
  - \(\mu\): mean (expected response time)  
  - \(\sigma\): dispersion (variability in response time)  

Exponentiated coefficients can be interpreted as multiplicative changes in expected response time (e.g., 1.10 = +10%, 0.90 = −10%).

---

### Model Specification

As for eye-tracking outcomes, models included semantic predictors, ABM condition, and perfectionism, along with their interactions. Only the **semantic contrasts that significantly interacted with perfectionism in Study 1** were retained.

The corresponding **pre-ABM response time** was included as a covariate to control for baseline differences.

#### Mean Submodel (\(\mu\))

\[
\log(\mu_{ij}) =
\beta_0
+ \beta_1 PreAB_{ij}
+ \beta_2 SC_{ij}
+ \beta_3 Perf_j
+ \beta_4 Cond_j
+ \beta_5 (SC_{ij} \times Perf_j)
+ \beta_6 (SC_{ij} \times Cond_j)
+ \beta_7 (Perf_j \times Cond_j)
+ \beta_8 (SC_{ij} \times Perf_j \times Cond_j)
+ f_1(\text{subject}_j)
+ f_2(\text{block}_i)
\]

where:

- \(\mu_{ij}\): expected response time for trial \(i\) and participant \(j\)  
- \(PreAB_{ij}\): pre-ABM response time (baseline covariate)  
- \(SC_{ij}\): retained semantic contrast (e.g., Emotional Valence or Performance Relevance)  
- \(Perf_j\): perfectionism (Perfectionistic Strivings or Concerns; modeled separately, mean-centered)  
- \(Cond_j\): ABM condition (control, success, failure)  
- \(f_1, f_2\): penalized smooth terms for participant and block  

---

#### Dispersion Submodel (\(\sigma\))

\[
\log(\sigma_{ij}) =
\gamma_0
+ \gamma_1 BR_{ij}
+ \gamma_2 Cond_j
\]

where:

- \(\sigma_{ij}\): dispersion (variability in response time)  
- \(BR_{ij}\): rule awareness (0 = no, 1 = yes)  
- \(Cond_j\): ABM condition  

---

ABM condition was included in the dispersion submodel to account for potential condition-dependent differences in the variability of response times, beyond effects on the mean.

---

### Data Preparation for Gamma Models

To reduce memory usage and computation time, a subset containing only variables required for model fitting was created.

```{r subset_rt_data_study2}
sub_rt_qu2 <- rt_qu2[c("subject_nr_1", "response_time_1", "guessed_block_rule_1", 
                       "subject_nr_2","response_time_2", "guessed_block_rule_2", 
                       "block_loop", "Change_category_PR_SvsF", 
                       "Change_category_PR_LvsH", "Change_category_EV", 
                       "Condition","Perf_Strivings_c" , "Perf_Concerns_c")]
```

### 7. Response Time

Response time was modeled using a **gamma GAMLSS** with a **log** link for the mean parameter, as in Study 1.

##### gm0_response_time_2

**Baseline model**

```{r gm0_response_time_2_study2}
gm0_response_time_2 <- gamlss(
  response_time_2 ~ 
    response_time_1 +
    pb(subject_nr_2) + 
    pb(block_loop),
  family = GA(mu.link = "log"),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  data = na.omit(sub_rt_qu2)
)
summary(gm0_response_time_2)
```

**Exponentiated coefficients (gm0)**

```{r gm0_response_time_2_coef_study2}
print(round(exp(gm0_response_time_2$mu.coefficients),4))
```


##### gm1.1_response_time_2

**Partial model: Perfectionistic Strivings**

Following Study 1, the partial model retained Performance Relevance (success vs. failure), ABM condition, and the Performance Relevance × Perfectionistic Strivings interaction.

```{r gm1.1_response_time_2_study2}
gm1.1_response_time_2 <- gamlss(
  response_time_2 ~ 
    response_time_1 +
    Condition +
    Change_category_PR_SvsF * Perf_Strivings_c + 
    pb(subject_nr_2) + 
    pb(block_loop),
  family = GA(mu.link = "log"),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  data = na.omit(sub_rt_qu2)
)
summary(gm1.1_response_time_2)
```

**Exponentiated coefficients (gm1.1)**

```{r gm1.1_response_time_2_coef_study2}
print(round(exp(gm1.1_response_time_2$mu.coefficients),4))
```

**Comparison of model fit (gm1.1 vs. gm0)**

```{r gm1.1_response_time_2_fit_study2}
lrtest(gm0_response_time_2, gm1.1_response_time_2)

AIC(gm0_response_time_2, gm1.1_response_time_2)
```


##### gm2.1_response_time_2

**Full model: Perfectionistic Strivings**

The full model added the three-way interaction between Performance Relevance, ABM condition, and Perfectionistic Strivings.

```{r gm2.1_response_time_2_study2}
gm2.1_response_time_2 <- gamlss(
  response_time_2 ~ 
    response_time_1 +
    Change_category_PR_SvsF * Perf_Strivings_c * Condition + 
    pb(subject_nr_2) + 
    pb(block_loop),
  family = GA(mu.link = "log"),
  sigma.formula = ~ guessed_block_rule_2 + Condition,
  data = na.omit(sub_rt_qu2)
)
summary(gm2.1_response_time_2)
```

**Exponentiated coefficients (gm2.1))**

```{r gm2.1_response_time_2_coef_study2}
print(round(exp(gm2.1_response_time_2$mu.coefficients),4))
```

**Comparison of model fit (gm2.1 vs. gm1.1)**

```{r gm2.1_response_time_2_fit_study2}
lrtest(gm1.1_response_time_2, gm2.1_response_time_2)

AIC(gm1.1_response_time_2, gm2.1_response_time_2)
```

**Model diagnostics (gm2.1)**

```{r gm2.1_response_time_2_resid_study2, fig.height= 4, fig.width=10}
p1 <- diag_resid_fitted(gm2.1_response_time_2)
p2 <- diag_ppc_gamma(gm2.1_response_time_2)

grid.arrange(p1, p2, ncol = 2)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Path *c′*: Moderating Effect of ABM Condition on Perfectionism → Mood Change

Path c′ examined whether **ABM condition moderated the relationship between perfectionism and mood change**. Mood outcomes were analyzed separately for **positive** and **negative** affect using **multiple linear regression**.

Two sets of analyses were conducted:

- **Control analyses:** mood change from **pre- to post-ABM**  
- **Main analyses:** mood change from **pre- to post-Tangram** (i.e., after the failure induction)

All models included:

- **Perfectionistic Strivings** and **Perfectionistic Concerns**
- **ABM condition**
- the interaction terms between perfectionism and ABM condition
- **baseline depressive symptoms (CES-D)** and **baseline anxiety symptoms (GAD-7)** as covariates

ABM condition was treated as a categorical predictor, with additional releveling used in follow-up models to decompose significant interactions.

## Model Specification

### General Model

\[
Mood_j =
\beta_0
+ \beta_1 PS_j
+ \beta_2 PC_j
+ \beta_3 Cond_j
+ \beta_4 (PS_j \times Cond_j)
+ \beta_5 (PC_j \times Cond_j)
+ \beta_6 CESD_j
+ \beta_7 GAD7_j
+ \varepsilon_j
\]

where:

- \(Mood_j\): mood change score for participant \(j\)
- \(PS_j\): Perfectionistic Strivings for participant \(j\)
- \(PC_j\): Perfectionistic Concerns for participant \(j\)
- \(Cond_j\): ABM condition (Control, Success, Failure)
- \(CESD_j\): baseline depressive symptoms
- \(GAD7_j\): baseline anxiety symptoms
- \(\varepsilon_j\): residual error

Because these models were estimated at the participant level, no random effects were included.

## Control Analyses: Mood Change from Pre- to Post-ABM

These analyses tested whether ABM condition was associated with immediate changes in mood before the failure induction.

### lm0.1_positive

**1. Positive Mood Change (pre- to post-ABM)**

```{r lm0.1_positive}
lm0.1_positive <- lm(
  POS_23 ~ 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7, 
  data = qu2
)
summary(lm0.1_positive)
```

### lm0.2_negative 

**2. Negative Mood Change (pre- to post-ABM)**

```{r lm0.2_negative}
lm0.2_negative <- lm(
  NEG_23 ~ 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7, 
  data = qu2
)
summary(lm0.2_negative)
```

**Decomposition of the interaction between Perfectionistic Concerns and ABM Condition**

#### lm0.2a_negative 

**ABM Condition = Success**

```{r lm0.2a_negative}
qu2$Condition_S <- relevel(qu2$Condition, ref = "Success")

lm0.2a_negative <- lm(
  NEG_23 ~ 
    Perf_Strivings_c * Condition_S +
    Perf_Concerns_c * Condition_S +
    CESD + GAD7, 
  data = qu2
)
summary(lm0.2a_negative)
```

#### lm0.2b_negative 

**ABM Condition = Failure**

```{r lm0.2b_negative}
qu2$Condition_F <- relevel(qu2$Condition, ref = "Failure")

lm0.2b_negative <- lm(
  NEG_23 ~ 
    Perf_Strivings_c * Condition_F +
    Perf_Concerns_c * Condition_F +
    CESD + GAD7, 
  data = qu2
)
summary(lm0.2b_negative)
```

## Main Analyses: Mood Change from Pre- to Post-Tangram

These models tested whether ABM condition moderated the relationship between perfectionism and emotional response to the failure induction.

### lm1.1_positive

**3. Positive Mood Change (pre- to post-Tangram)**

```{r lm1.1_positive_mood_study2}
lm1.1_positive <- lm(
  POS_34 ~ 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.1_positive)
```

**Decomposition of the interaction between Perfectionistic Strivings and Condition**

#### lm1.1a_positive

**ABM Condition = Success**

```{r lm1.1a_positive}
qu2$Condition_S <- relevel(qu2$Condition, ref = "Success")

lm1.1a_positive <- lm(
  POS_34 ~ 
    Perf_Strivings_c * Condition_S +
    Perf_Concerns_c * Condition_S +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.1a_positive)
```

#### lm1.1b_positive

**ABM Condition = Failure**

```{r lm1.1b_positive}
qu2$Condition_F <- relevel(qu2$Condition, ref = "Failure")
lm1.1b_positive <- lm(
  POS_34 ~ 
    Perf_Strivings_c * Condition_F +
    Perf_Concerns_c * Condition_F +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.1b_positive)
```

**Model diagnostics (positive mood)**

```{r lm1.1_positive_resid_study2, fig.width = 10, fig.height = 10}
par(mfrow = c(2, 2))
plot(lm1.1_positive)

res_lm1.1_positive <- resid(lm1.1_positive)
stat.desc(res_lm1.1_positive, norm = TRUE)
```

### lm1.2_negative

**4. Negative Mood Change (pre- to post-Tangram)**

```{r lm1.2_negative}
lm1.2_negative <- lm(
  NEG_34 ~ 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.2_negative)
```

**Decomposition of the interaction between Perfectionistic Strivings and Condition**

#### lm1.2a_negative

**ABM Condition = Success**

```{r lm1.2a_negative}
qu2$Condition_S <- relevel(qu2$Condition, ref = "Success")

lm1.2a_negative <- lm(
  POS_34 ~ 
    Perf_Strivings_c * Condition_S +
    Perf_Concerns_c * Condition_S +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.2a_negative)
```

#### lm1.2b_negative

**ABM Condition = Failure**

```{r lm1.2b_negative}
qu2$Condition_F <- relevel(qu2$Condition, ref = "Failure")
lm1.2b_negative <- lm(
  POS_34 ~ 
    Perf_Strivings_c * Condition_F +
    Perf_Concerns_c * Condition_F +
    CESD + GAD7, 
  data = qu2
)
summary(lm1.2b_negative)
```

**Model diagnostics (negative mood)**

```{r lm1.2_negative_resid_study2, fig.width = 10, fig.height = 10}
par(mfrow = c(2, 2))
plot(lm1.2_negative)

res_lm1.2_negative <- resid(lm1.2_negative)
stat.desc(res_lm1.2_negative, norm = TRUE)
```

**Interaction plots**

To visualize the associations between perfectionism and mood change across ABM conditions, interaction plots were generated separately for positive and negative mood, and for Perfectionistic Strivings and Perfectionistic Concerns.

```{r lm1_interaction_plot_study2, fig.width=15, fig.height=10}
lm2.1_positive <- lm(
  POS_34 ~ Perf_Strivings_c * Condition,
  data = qu2
)

ip_pos_1 <- plot_model(
  lm2.1_positive,
  type = "int",
  mdrt.values = "all",
  ci.lvl = NA,
  legend.title = "ABM Condition"
) + 
  labs(
    title = "Positive Mood After Tangram Task",
    x = "Perfectionistic Strivings",
    y = ""
  ) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

lm2.1_negative <- lm(
  NEG_34 ~ Perf_Strivings_c * Condition,
  data = qu2
)

ip_neg_1 <- plot_model(
  lm2.1_negative,
  type = "int",
  mdrt.values = "all",
  ci.lvl = NA,
  legend.title = "ABM Condition"
) + 
  labs(
    title = "Negative Mood After Tangram Task",
    x = "Perfectionistic Strivings",
    y = ""
  ) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

lm2.2_positive <- lm(
  POS_34 ~ Perf_Concerns_c * Condition,
  data = qu2
)

ip_pos_2 <- plot_model(
  lm2.2_positive,
  type = "int",
  mdrt.values = "all",
  ci.lvl = NA,
  legend.title = "ABM Condition"
) + 
  labs(
    title = "Positive Mood After Tangram Task",
    x = "Perfectionistic Concerns",
    y = ""
  ) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

lm2.2_negative <- lm(
  NEG_34 ~ Perf_Concerns_c * Condition,
  data = qu2
)

ip_neg_2 <- plot_model(
  lm2.2_negative,
  type = "int",
  mdrt.values = "all",
  ci.lvl = NA,
  legend.title = "ABM Condition"
) + 
  labs(
    title = "Negative Mood After Tangram Task",
    x = "Perfectionistic Concerns",
    y = ""
  ) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

grid.arrange(
  ip_pos_1, ip_neg_1,
  ip_pos_2, ip_neg_2,
  ncol = 2, nrow = 2
)
```
