---
title: "Appendix B"
subtitle: "Study 2 - Attention Bias Manipulation"
author: "MM"
date: "`r Sys.Date()`"
knit: (function(input_file, encoding) { output_file <- rmarkdown::render(input_file, encoding = encoding); dependency_dir <- sub("\\.html$", "_files", output_file); if (dir.exists(dependency_dir)) unlink(dependency_dir, recursive = TRUE, force = TRUE); output_file })
output:
  html_document:
    toc: true
    code_folding: hide
    self_contained: true

editor_options:
  markdown:
    wrap: 72
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	eval = TRUE,
	message = FALSE,
	warning = FALSE,
	digits = 3
)
# Load libraries
library(rmarkdown)
library(readxl) # For reading excel files
library(dplyr) # For reshaping and summarizing data

library(ggplot2) # For plots
library(gridExtra) # For arranging ggplots in a grid
library(grid) # For grob functions
library(sjPlot) # For plotting interactions
library(ggeffects) # For model-based predictions
library(emmeans) # For planned comparisons

library(psych) # For Cronbach's alpha and McDonald's omega
library(pastecs) # For testing normality assumptions

library(glmmTMB) # For beta and gamma generalized linear mixed models
library(lme4) # For lmm fitting
library(lmtest) # For likelihood ratio tests

```

# Data Preparation

This section documents the main preprocessing steps used to derive the variables analyzed in Study 2. Consistent with the manuscript, data preparation for perfectionism and attentional measures followed the same procedures as in Study 1. This section therefore focuses on the Study 2-specific extensions, namely repeated mood assessments and pre–post attentional data.

## Questionnaire data

Perfectionism was assessed using the Hewitt and Flett Multidimensional Perfectionism Scale (HMPS) and the Frost Multidimensional Perfectionism Scale (FMPS). As in Study 1, item scoring, reverse coding, and computation of questionnaire totals followed the standard scoring procedures for each instrument.

Psychological distress was assessed repeatedly using seven Visual Analog Mood Scales (VAMS; 0–9). In line with the manuscript, these items were aggregated into Positive Mood (happy, excited, positive mood) and Negative Mood (sad, anxious, angry, negative mood) scores. Baseline depressive and anxiety symptoms were assessed using the CES-D and GAD-7 and were retained as control variables.

```{r read_data_questionnaires_study2, include=FALSE}
# Read data
qu2.1 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.1.xlsx")
qu2.2 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.2.xlsx")
qu2.3_1 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_1.xlsx")
qu2.3_2 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_2.xlsx")
qu2.3_3 <- read_excel("AB_Perfectionism_Data/questionnaires_study2.3_3.xlsx")

# Merge questionnaire files
qu2a <- qu2.1 %>% inner_join(qu2.2, by = "ID")
qu2b <- qu2.3_1 %>% inner_join(qu2.3_2, by = "ID") %>% inner_join(qu2.3_3, by = "ID")
qu2 <- qu2a %>% inner_join(qu2b, by = "ID")

# Gender was retained in the consolidated export but not in the split files.
# Import it only for the sample-characteristics table; it is not used in any
# inferential model.
qu2_demographics <- read_excel("AB_Perfectionism_Data/questionnaires_study2.xlsx") %>%
  select(ID, any_of("Genre")) %>%
  distinct(ID, .keep_all = TRUE)
qu2 <- qu2 %>% left_join(qu2_demographics, by = "ID")
qu2$Age <- as.numeric(qu2$Age)
```

  
```{r qu_scores_study2}
# HMPS reverse coding
qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_8", "HMPS_9", "HMPS_10", "HMPS_12",
        "HMPS_19", "HMPS_21", "HMPS_24", "HMPS_30", "HMPS_34", "HMPS_36", "HMPS_37",
        "HMPS_38", "HMPS_43", "HMPS_44", "HMPS_45")] <-
  8 - qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_8", "HMPS_9", "HMPS_10", "HMPS_12",
              "HMPS_19", "HMPS_21", "HMPS_24", "HMPS_30", "HMPS_34", "HMPS_36", "HMPS_37",
              "HMPS_38", "HMPS_43", "HMPS_44", "HMPS_45")]

# HMPS subscales
SOP <- qu2[, c("HMPS_1", "HMPS_6", "HMPS_8", "HMPS_12", "HMPS_14", "HMPS_15", "HMPS_17",
               "HMPS_20", "HMPS_23", "HMPS_28", "HMPS_32", "HMPS_34", "HMPS_36", "HMPS_40", "HMPS_42")]
OOP <- qu2[, c("HMPS_2", "HMPS_3", "HMPS_4", "HMPS_7", "HMPS_10", "HMPS_16", "HMPS_19",
               "HMPS_22", "HMPS_24", "HMPS_26", "HMPS_27", "HMPS_29", "HMPS_38", "HMPS_43", "HMPS_45")]
SPP <- qu2[, c("HMPS_5", "HMPS_9", "HMPS_11", "HMPS_13", "HMPS_18", "HMPS_21", "HMPS_25",
               "HMPS_30", "HMPS_31", "HMPS_33", "HMPS_35", "HMPS_37", "HMPS_39", "HMPS_41", "HMPS_44")]

qu2$SOP <- rowSums(SOP)
qu2$OOP <- rowSums(OOP)
qu2$SPP <- rowSums(SPP)

# FMPS subscales
PS <- qu2[, c("FMPS_4", "FMPS_6", "FMPS_12", "FMPS_16", "FMPS_19", "FMPS_24", "FMPS_30")]
PE <- qu2[, c("FMPS_1", "FMPS_11", "FMPS_15", "FMPS_20", "FMPS_26")]
PC <- qu2[, c("FMPS_3", "FMPS_5", "FMPS_22", "FMPS_35")]
CM <- qu2[, c("FMPS_9", "FMPS_10", "FMPS_13", "FMPS_14", "FMPS_18", "FMPS_21", "FMPS_23", "FMPS_25", "FMPS_34")]
DA <- qu2[, c("FMPS_17", "FMPS_28", "FMPS_32", "FMPS_33")]
O  <- qu2[, c("FMPS_2", "FMPS_7", "FMPS_8", "FMPS_27", "FMPS_29", "FMPS_31")]

qu2$PS <- rowSums(PS)
qu2$PE <- rowSums(PE)
qu2$PC <- rowSums(PC)
qu2$CM <- rowSums(CM)
qu2$DA <- rowSums(DA)
qu2$O  <- rowSums(O)

# VAMS composites
POS_1 <- qu2[, c("VAMS1_1", "VAMS1_6", "VAMS1_7")]
NEG_1 <- qu2[, c("VAMS1_2", "VAMS1_3", "VAMS1_4", "VAMS1_5")]
POS_2 <- qu2[, c("VAMS2_1", "VAMS2_6", "VAMS2_7")]
NEG_2 <- qu2[, c("VAMS2_2", "VAMS2_3", "VAMS2_4", "VAMS2_5")]
POS_3 <- qu2[, c("VAMS3_1", "VAMS3_6", "VAMS3_7")]
NEG_3 <- qu2[, c("VAMS3_2", "VAMS3_3", "VAMS3_4", "VAMS3_5")]
POS_4 <- qu2[, c("VAMS4_1", "VAMS4_6", "VAMS4_7")]
NEG_4 <- qu2[, c("VAMS4_2", "VAMS4_3", "VAMS4_4", "VAMS4_5")]

qu2$POS_1 <- rowSums(POS_1)
qu2$NEG_1 <- rowSums(NEG_1)
qu2$POS_2 <- rowSums(POS_2)
qu2$NEG_2 <- rowSums(NEG_2)
qu2$POS_3 <- rowSums(POS_3)
qu2$NEG_3 <- rowSums(NEG_3)
qu2$POS_4 <- rowSums(POS_4)
qu2$NEG_4 <- rowSums(NEG_4)

# CES-D reverse coding and totals
qu2[, c("CESD_4", "CESD_8", "CESD_12", "CESD_16")] <-
  3 - qu2[, c("CESD_4", "CESD_8", "CESD_12", "CESD_16")]

CESD <- qu2[, c("CESD_1", "CESD_2", "CESD_3", "CESD_4", "CESD_5", "CESD_6", "CESD_7", "CESD_8",
                "CESD_9", "CESD_10", "CESD_11", "CESD_12", "CESD_13", "CESD_14", "CESD_15",
                "CESD_16", "CESD_17", "CESD_18", "CESD_19", "CESD_20")]
qu2$CESD <- rowSums(CESD)

# GAD-7 totals
qu2$GAD7_1 <- as.numeric(qu2$GAD7_1)
qu2$GAD7_2 <- as.numeric(qu2$GAD7_2)
qu2$GAD7_3 <- as.numeric(qu2$GAD7_3)
qu2$GAD7_4 <- as.numeric(qu2$GAD7_4)
qu2$GAD7_5 <- as.numeric(qu2$GAD7_5)
qu2$GAD7_6 <- as.numeric(qu2$GAD7_6)
qu2$GAD7_7 <- as.numeric(qu2$GAD7_7)

GAD7 <- qu2[, c("GAD7_1", "GAD7_2", "GAD7_3", "GAD7_4", "GAD7_5", "GAD7_6", "GAD7_7")]
qu2$GAD7 <- rowSums(GAD7)
```


### Outlier Handling

Outliers were identified before computing descriptive statistics and correlations. Following the same procedure as in Study 1, univariate outliers were defined as observations with standardized scores below -3 or above +3, and multivariate outliers were assessed using Mahalanobis distance. 

```{r boxplots_study2, fig.width = 18, fig.height= 8}
par(mfrow=c(1,2))
boxplot(qu2[, c("SOP", "OOP","SPP", "PS", "PC", "PE", "CM", "DA", "O", "CESD", "GAD7")])
boxplot(qu2[, c("POS_1", "NEG_1", "POS_2", "NEG_2","POS_3", "NEG_3", "POS_4", "NEG_4")])
```

```{r outliers_study2}
# Standardize questionnaire variables
qu2[, c("ZSOP", "ZOOP", "ZSPP", "ZPS", "ZPC", "ZPE", "ZCM", "ZDA", "ZO", "ZGAD7", "ZCESD",
        "ZPOS_1", "ZNEG_1", "ZPOS_2", "ZNEG_2", "ZPOS_3", "ZNEG_3", "ZPOS_4", "ZNEG_4")] <-
  scale(qu2[, c("SOP", "OOP", "SPP", "PS", "PC", "PE", "CM", "DA", "O", "GAD7", "CESD",
                "POS_1", "NEG_1", "POS_2", "NEG_2", "POS_3", "NEG_3", "POS_4", "NEG_4")])

# Identify univariate outliers
univar_out <- c(
  which(qu2$ZSOP > 3 | qu2$ZSOP < -3),
  which(qu2$ZOOP > 3 | qu2$ZOOP < -3),
  which(qu2$ZSPP > 3 | qu2$ZSPP < -3),
  which(qu2$ZPS > 3 | qu2$ZPS < -3),
  which(qu2$ZPE > 3 | qu2$ZPE < -3),
  which(qu2$ZPC > 3 | qu2$ZPC < -3),
  which(qu2$ZCM > 3 | qu2$ZCM < -3),
  which(qu2$ZDA > 3 | qu2$ZDA < -3),
  which(qu2$ZO > 3 | qu2$ZO < -3),
  which(qu2$ZGAD7 > 3 | qu2$ZGAD7 < -3),
  which(qu2$ZCESD > 3 | qu2$ZCESD < -3),
  which(qu2$ZPOS_1 > 3 | qu2$ZPOS_1 < -3),
  which(qu2$ZNEG_1 > 3 | qu2$ZNEG_1 < -3),
  which(qu2$ZPOS_2 > 3 | qu2$ZPOS_2 < -3),
  which(qu2$ZNEG_2 > 3 | qu2$ZNEG_2 < -3),
  which(qu2$ZPOS_3 > 3 | qu2$ZPOS_3 < -3),
  which(qu2$ZNEG_3 > 3 | qu2$ZNEG_3 < -3),
  which(qu2$ZPOS_4 > 3 | qu2$ZPOS_4 < -3),
  which(qu2$ZNEG_4 > 3 | qu2$ZNEG_4 < -3)
)

univar_out <- unique(univar_out)

# Remove univariate outliers
qu2 <- qu2[-univar_out, ]

# Identify multivariate outliers
vars <- qu2[, c("SOP", "OOP", "SPP", "PS", "PC", "PE", "CM", "DA", "O",
                "POS_1", "NEG_1", "POS_2", "NEG_2", "POS_3", "NEG_3", "POS_4", "NEG_4")]
md <- mahalanobis(vars, center = colMeans(vars), cov = cov(vars))
cutoff <- qchisq(p = 1 - .001, df = ncol(vars))
multivar_out_MH <- which(md > cutoff)

length(multivar_out_MH)

# Remove one participant flagged administratively as outlier in the condition variable
which(qu2$Condition == "Outlier")
qu2 <- qu2[-which(qu2$Condition == "Outlier"), ]
```

Univariate outliers were excluded from subsequent analyses. No multivariate outliers were identified.

### Perfectionism Dimensions

Following the same procedure as in Study 1, Perfectionistic Strivings was computed as the sum of standardized Personal Standards (FMPS-PS) and Self-Oriented Perfectionism (HMPS-SOP) scores. Perfectionistic Concerns was computed as the sum of standardized Concerns over Mistakes (FMPS-CM), Doubts about Actions (FMPS-DA), and Socially Prescribed Perfectionism (HMPS-SPP) scores.
        
```{r strivings_concerns_study2}
qu2$Perf_Strivings <- rowSums(qu2[, c("ZPS", "ZSOP")])
qu2$Perf_Concerns  <- rowSums(qu2[, c("ZCM", "ZDA", "ZSPP")])
```

### Mood Outcomes

Positive and negative emotion scores were computed as sums of the corresponding VAMS items at each assessment. The primary analyses operationalized emotional reactivity using post-assessment mood conditional on the corresponding score at the immediately preceding assessment: post-ABM mood was adjusted for pre-ABM mood, and post-Tangram mood was adjusted for mood immediately before the Tangram task.

Questionnaire descriptives and correlations are
calculated below after identifying the common attention-task analytic sample.

## Attention Bias Measurement

Attentional data were collected at two time points, before (t1) and after (t2) the ABM procedure. As in Study 1, attention bias was assessed using the FV-FICB task with word stimuli from five semantic categories: Success, Failure, Positive, Negative, and Neutral.

### Response Times

Response times were defined as the latency between onset of the changed display and the participant’s response. Trial presentation order was retained as `trial_nr`; the ordering of the RT rows was verified against `TRIAL_INDEX` in the raw eye-tracking records. Analyses were conducted on correct trials only, and trials with response times below 200 ms were excluded.

```{r read_data_rt_study2, include=FALSE}
rt2 <- read_excel("AB_Perfectionism_Data/rt_study2.xlsx") %>%
  rename(subject_id = subject_nr, block_id = block_loop)

# Number blocks by their order of presentation within each participant and
# measurement occasion. block_id uniquely identifies each block,
# including paired blocks with the same change category.
rt2 <- rt2 %>%
  group_by(subject_id, Temps_de_mesure) %>%
  mutate(block_nr = match(block_id, unique(block_id)),
         trial_nr = row_number()) %>%
  ungroup()
```

### Correct Responses

Correct responses were recorded when participants accurately identified the changed word.

```{r data_preparation_rt_study2}
rt2$correct_response <- as.factor(rt2$correct_response) %>%
  dplyr::recode("Vrai" = 1, "Faux" = 0)

correct_responses <- rt2[,c("subject_id", "correct_response", "Temps_de_mesure")] %>% group_by(subject_id, Temps_de_mesure) %>% summarize(correct_response = sum(correct_response))

incorrect <- which(rt2$correct_response == 0)
rt200 <- which(rt2$response_time < 200)

length(incorrect)
length(rt200)

rt2$response_time[c(incorrect, rt200)] <- NA
```

Rule awareness was assessed at the end of each block and coded as a binary variable (0 = no, 1 = yes). This variable was used to model dispersion in subsequent manipulation check analyses.

```{r guessed_block_rule_study2}
 rt2 <- rt2 %>% rename(guessed_block_rule = response_keyboard_response)
rt2$guessed_block_rule <- as.factor(rt2$guessed_block_rule) %>%
  dplyr::recode("o" = 1, "O" = 1, "n" = 0, "N" = 0)
```

For manipulation checks, response-time data were reshaped to a paired T1-T2 format so that post-ABM outcomes could be modeled conditional on their corresponding pre-ABM values.

```{r short_format_rt_study2}
 t1 <- which(rt2$Temps_de_mesure == "T1")
t2 <- which(rt2$Temps_de_mesure == "T2")

rt2_1 <- rt2[t1, ]
rt2_2 <- rt2[t2, ]

drop <- c("Temps_de_mesure", "ID", "datetime", "response_position", "participant_response", "correct_response")

rt2_1 <- rt2_1[, !(names(rt2_1) %in% drop)] %>%
  rename(subject_id_1 = subject_id,
         block_nr_1 = block_nr,
         trial_nr_1 = trial_nr,
         response_time_1 = response_time,
         guessed_block_rule_1 = guessed_block_rule)

rt2_2 <- rt2_2[, !(names(rt2_2) %in% drop)] %>%
  rename(subject_id_2 = subject_id,
         block_nr_2 = block_nr,
         trial_nr_2 = trial_nr,
         response_time_2 = response_time,
         guessed_block_rule_2 = guessed_block_rule)

rt <- rt2_1 %>%
  inner_join(
    rt2_2,
    by = c("Code", "Change_category", "Change_location", "Change_word", "Flicker_word",
           "A", "B", "C", "D", "E",
           "OS_A_word", "OS_B_word", "OS_C_word", "OS_D_word", "OS_E_word",
           "CS_A_word", "CS_B_word", "CS_C_word", "CS_D_word", "CS_E_word", "block_id"),
    relationship = "one-to-one"
  )

message("Paired RT participants: ", n_distinct(rt$Code), " of ",
        n_distinct(intersect(rt2_1$Code, rt2_2$Code)),
        " participants represented at both assessments.")

```


```{r merge_rt_qu_study2, include = FALSE}
# Merge rt data with questionnaire data
rt_qu2 <- rt[c("Code", "block_id", "block_nr_1", "block_nr_2", "Change_category",
               "subject_id_1", "trial_nr_1", "response_time_1", "guessed_block_rule_1", 
               "subject_id_2", "trial_nr_2", "response_time_2", "guessed_block_rule_2")]  %>% 
  rename(ID = Code) %>%
  inner_join(qu2[c("ID", "Condition", "Perf_Strivings", "Perf_Concerns",
                   "CESD", "GAD7",
                   "Age", "Sexe", "Statut","Actual_Studies","University_HE",
                   "Actual_Program","DomaineTravail", "Mother_Tongue")], 
             relationship = "many-to-many")
```

### Eye Tracking

Eye movements during the free-viewing phase were used to compute the attentional indices. As in Study 1, raw eye-tracking data were recoded prior to index construction, and indices were aggregated at the block level.

```{r read_data_et_study2, include=FALSE}
et2 <- read_excel("AB_Perfectionism_Data/et_study2_500to5500.xlsx")
#for merging later
et2 <- et2 %>% rename(subject_id = RECORDING_SESSION_LABEL)
```

```{r data_preparation_et_study2, include=FALSE}
et2$IA_LABEL <- as.factor(et2$IA_LABEL)
et2$IA_LABEL <- et2$IA_LABEL %>%
  dplyr::recode("Neutre" = "Neutral",
                "Pos" = "Positive",
                "Neg" = "Negative",
                "Pos_Perf" = "Success",
                "Neg_Perf" = "Failure")

et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- as.factor(et2$IA_FIRST_FIXATION_VISITED_IA_COUNT)
et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- et2$IA_FIRST_FIXATION_VISITED_IA_COUNT %>%
  dplyr::recode("0" = "1", "1" = "1", "2" = "0", "3" = "0", "4" = "0")
et2$IA_FIRST_FIXATION_VISITED_IA_COUNT <- as.numeric(as.character(et2$IA_FIRST_FIXATION_VISITED_IA_COUNT))

et2$IA_FIRST_FIXATION_TIME <- as.numeric(et2$IA_FIRST_FIXATION_TIME)
```

As in Study 1, the following block-level indices were derived: probability of first or second fixation, latency to first fixation, and dwell time. Dwell time was computed for the whole trial and separately for the early, intermediate, and late viewing phases.

```{r calculate_et_indices_study2}
# Merge ET with RT to recover block-level rule variables. EyeLink TRIAL_INDEX
# corresponds to trial_nr within each participant and measurement occasion.
rt_block_lookup2 <- rt2 %>%
  select(Temps_de_mesure, subject_id, trial_nr, Change_category, Code,
         block_id, block_nr, guessed_block_rule) %>%
  distinct()

etrt2 <- et2 %>%
  rename(trial_nr = TRIAL_INDEX) %>%
  left_join(rt_block_lookup2,
            by = c("MEASUREMENT_TIME" = "Temps_de_mesure", "subject_id",
                   "trial_nr", "Change_category"),
            relationship = "many-to-one") %>%
  rename(Temps_de_mesure = MEASUREMENT_TIME)

et2a <- etrt2[c("Temps_de_mesure", "Code", "subject_id", "block_id", "block_nr", "IA_LABEL", "Change_category", "guessed_block_rule",
                "IA_DWELL_TIME", "IA_DWELL_TIME_500to1500", "IA_DWELL_TIME_1500to3500", "IA_DWELL_TIME_3500to5500",
                "IA_FIRST_FIXATION_VISITED_IA_COUNT", "IA_FIRST_FIXATION_TIME")] %>%
  group_by(Temps_de_mesure, Code, subject_id, block_id, block_nr, IA_LABEL, Change_category, guessed_block_rule) %>%
  reframe(
    IA_FIRST_FIXATION_PROBABILITY = mean(na.omit(IA_FIRST_FIXATION_VISITED_IA_COUNT)),
    IA_FIRST_FIXATION_TIME_BLOCKMEAN = mean(na.omit(IA_FIRST_FIXATION_TIME)),
    IA_DWELL_TIME_BLOCKMEAN = mean(IA_DWELL_TIME),
    IA_DWELL_TIME_500to1500_BLOCKMEAN = mean(IA_DWELL_TIME_500to1500),
    IA_DWELL_TIME_1500to3500_BLOCKMEAN = mean(IA_DWELL_TIME_1500to3500),
    IA_DWELL_TIME_3500to5500_BLOCKMEAN = mean(IA_DWELL_TIME_3500to5500)
  )

et2b <- et2a %>%
  group_by(Temps_de_mesure, subject_id, block_id, block_nr) %>%
  summarise(
    AVG_FIRST_FIXATION_TIME = sum(na.omit(IA_FIRST_FIXATION_TIME_BLOCKMEAN)),
    AVG_DWELL_TIME = sum(IA_DWELL_TIME_BLOCKMEAN),
    AVG_DWELL_TIME_500to1500 = sum(IA_DWELL_TIME_500to1500_BLOCKMEAN),
    AVG_DWELL_TIME_1500to3500 = sum(IA_DWELL_TIME_1500to3500_BLOCKMEAN),
    AVG_DWELL_TIME_3500to5500 = sum(IA_DWELL_TIME_3500to5500_BLOCKMEAN)
  )

et2 <- et2a %>% inner_join(et2b, relationship = "many-to-many")

et2$first_fix_prob <- et2$IA_FIRST_FIXATION_PROBABILITY
et2$first_fix_latency <- et2$IA_FIRST_FIXATION_TIME_BLOCKMEAN / et2$AVG_FIRST_FIXATION_TIME
et2$dwell_time <- et2$IA_DWELL_TIME_BLOCKMEAN / et2$AVG_DWELL_TIME
et2$dwell_time_early <- et2$IA_DWELL_TIME_500to1500_BLOCKMEAN / et2$AVG_DWELL_TIME_500to1500
et2$dwell_time_intermediate <- et2$IA_DWELL_TIME_1500to3500_BLOCKMEAN / et2$AVG_DWELL_TIME_1500to3500
et2$dwell_time_late <- et2$IA_DWELL_TIME_3500to5500_BLOCKMEAN / et2$AVG_DWELL_TIME_3500to5500
```


```{r remove_missing_et_study2}
# Remove remaining missing values
missing_ffp2 <- which(is.na(et2$first_fix_prob))
missing_ffl2 <- which(is.na(et2$first_fix_latency))
missing_dte2 <- which(is.na(et2$dwell_time_early))
missing_dtl2 <- which(is.na(et2$dwell_time_late))

et2 <- et2[-unique(c(missing_ffp2, missing_ffl2, missing_dte2, missing_dtl2)), ]
```

For manipulation checks, eye-tracking data were reshaped to paired T1-T2 format so that post-ABM outcomes could be modeled conditional on their corresponding pre-ABM values.

```{r short_format_et_study2}
t1 <- which(et2$Temps_de_mesure == "T1")
t2 <- which(et2$Temps_de_mesure == "T2")

et2_1 <- et2[t1, ]
et2_2 <- et2[t2, ]

et2_1 <- et2_1[c("Code", "subject_id", "block_id", "block_nr", "IA_LABEL", "Change_category",
                 "guessed_block_rule", "first_fix_prob", "first_fix_latency", "dwell_time",
                 "dwell_time_early", "dwell_time_intermediate", "dwell_time_late")] %>%
  rename(subject_id_1 = subject_id,
         block_nr_1 = block_nr,
         first_fix_prob_1 = first_fix_prob,
         first_fix_latency_1 = first_fix_latency,
         dwell_time_1 = dwell_time,
         dwell_time_early_1 = dwell_time_early,
         dwell_time_intermediate_1 = dwell_time_intermediate,
         dwell_time_late_1 = dwell_time_late,
         guessed_block_rule_1 = guessed_block_rule)

et2_2 <- et2_2[c("Code", "subject_id", "block_id", "block_nr", "IA_LABEL", "Change_category",
                 "guessed_block_rule", "first_fix_prob", "first_fix_latency", "dwell_time",
                 "dwell_time_early", "dwell_time_intermediate", "dwell_time_late")] %>%
  rename(subject_id_2 = subject_id,
         block_nr_2 = block_nr,
         first_fix_prob_2 = first_fix_prob,
         first_fix_latency_2 = first_fix_latency,
         dwell_time_2 = dwell_time,
         dwell_time_early_2 = dwell_time_early,
         dwell_time_intermediate_2 = dwell_time_intermediate,
         dwell_time_late_2 = dwell_time_late,
         guessed_block_rule_2 = guessed_block_rule)

et <- et2_1 %>%
  inner_join(
    et2_2,
    by = c("Code", "block_id", "IA_LABEL", "Change_category"),
    relationship = "one-to-one"
  )

message("Paired eye-tracking participants: ", n_distinct(et$Code), " of ",
        n_distinct(intersect(et2_1$Code, et2_2$Code)),
        " participants represented at both assessments.")

```

## Descriptive Statistics

All Study 2 analyses were restricted to participants represented in both the
paired response-time and paired eye-tracking datasets. Questionnaire variables
were retained at one row per participant, preventing repeated task observations
from weighting the participant-level descriptives or mood analyses.

```{r task_completer_questionnaire_sample_study2}
task_completer_ids <- inner_join(
  rt %>% distinct(ID = Code),
  et %>% distinct(ID = Code),
  by = "ID",
  relationship = "one-to-one"
)

qu2 <- qu2 %>%
  semi_join(task_completer_ids, by = "ID") %>%
  distinct(ID, .keep_all = TRUE)

stopifnot(nrow(qu2) == n_distinct(qu2$ID))
message("Study 2 common task-completer sample: N = ", nrow(qu2))

# Apply the same participant restriction to task-level objects created above.
rt2 <- rt2 %>% filter(Code %in% qu2$ID)
rt_qu2 <- rt_qu2 %>% semi_join(qu2 %>% distinct(ID), by = "ID")
correct_responses <- correct_responses %>%
  semi_join(rt2 %>% distinct(subject_id), by = "subject_id")
```

**Sample Demographics**

```{r sample_demographics_study2}
round(psych::describe(qu2$Age), 2)
table(qu2$Sexe, useNA = "ifany")
table(qu2$Genre, useNA = "ifany")
table(qu2$Actual_Studies, useNA = "ifany")
table(qu2$Mother_Tongue, useNA = "ifany")
```

**Questionnaires**

```{r descriptives_questionnaires_study2}
round(psych::describe(qu2[c(
  "SOP", "OOP", "SPP", "PS", "PE", "PC", "CM", "DA", "O",
  "Perf_Strivings", "Perf_Concerns", "CESD", "GAD7",
  "POS_1", "NEG_1", "POS_2", "NEG_2", "POS_3", "NEG_3",
  "POS_4", "NEG_4"
)]), 2)

corr_table <- corr.test(qu2[c("Perf_Strivings", "Perf_Concerns",
                              "POS_2", "NEG_2", "POS_3", "NEG_3",
                              "POS_4", "NEG_4", "CESD", "GAD7")])$stars
print(corr_table)
```

**Response Time**

```{r descriptives_rt_study2}
round(psych::describe(rt_qu2[c("response_time_1", "response_time_2")]), 2)

rt_qu2 %>%
  group_by(Change_category) %>%
  summarise(
    M_response_time_1 = round(mean(response_time_1, na.rm = TRUE), 2),
    SD_response_time_1 = round(sd(response_time_1, na.rm = TRUE), 2),
    M_response_time_2 = round(mean(response_time_2, na.rm = TRUE), 2),
    SD_response_time_2 = round(sd(response_time_2, na.rm = TRUE), 2),
    .groups = "drop"
  )
```

**Eye-Tracking Indices**

```{r merge_et_qu_study2, include=FALSE}
et_qu2 <- et %>%
  rename(ID = Code) %>%
  inner_join(
    qu2[c("ID", "Condition", "Perf_Strivings", "Perf_Concerns",
          "CESD", "GAD7",
          "Age", "Sexe", "Statut", "Actual_Studies", "University_HE",
          "Actual_Program", "DomaineTravail", "Mother_Tongue")],
    relationship = "many-to-many"
  )
```


```{r descriptives_et_indices_study2}
round(describe(et_qu2[c("first_fix_prob_1", "first_fix_latency_1", "dwell_time_1",
                        "dwell_time_early_1", "dwell_time_intermediate_1", "dwell_time_late_1")]), 2)

round(describe(et_qu2[c("first_fix_prob_2", "first_fix_latency_2", "dwell_time_2",
                        "dwell_time_early_2", "dwell_time_intermediate_2", "dwell_time_late_2")]), 2)
```

**Tangram Performance**

Tangram performance was operationalized as the number of correctly completed puzzles.

```{r descriptives_tangram_study2}
round(psych::describe(qu2$Tangrams), 2)
```

**Response Accuracy**

Response accuracy was defined as the number of trials in which the changed word was correctly identified. Descriptive statistics were computed separately for the pre-ABM (t1) and post-ABM (t2) assessments.

```{r descriptives_response_accuracy_study2}
accuracy <- correct_responses %>% group_by(subject_id, Temps_de_mesure) %>% summarize(correct_response = sum(correct_response))

accuracy_1 <- accuracy$correct_response[accuracy$Temps_de_mesure == "T1"]
accuracy_2 <- accuracy$correct_response[accuracy$Temps_de_mesure == "T2"]

describe(accuracy_1)
describe(accuracy_2)
```

**Rule Awareness**

Rule awareness was assessed at the end of each block and coded as a binary variable (0 = no, 1 = yes). For descriptive purposes, block-level responses were summed within time point, yielding the number of blocks in which participants reported awareness of the rule at t1 and t2.

```{r descriptives_rule_awareness_study2}
rule_awareness <- rt2 %>%
  group_by(subject_id, block_id, block_nr, Temps_de_mesure) %>%
  summarise(guessed_block_rule = mean(as.numeric(as.character(guessed_block_rule))), .groups = "drop") %>%
  group_by(subject_id, Temps_de_mesure) %>%
  summarise(guessed_block_rule = sum(guessed_block_rule), .groups = "drop")

rule_awareness_1 <- rule_awareness$guessed_block_rule[rule_awareness$Temps_de_mesure == "T1"]
rule_awareness_2 <- rule_awareness$guessed_block_rule[rule_awareness$Temps_de_mesure == "T2"]

round(describe(rule_awareness_1), 2)
round(describe(rule_awareness_2), 2)
```

## Distributional Inspection

To guide the choice of outcome distributions and link functions, the empirical distributions of the questionnaire, eye-tracking, and response-time variables were inspected visually using density plots. The mood plots show the observed composites used in the baseline-adjusted primary analyses. As in Study 1, this inspection was descriptive: model adequacy was evaluated from the conditional residuals rather than from the marginal outcome distributions alone.


```{r density_perfectionism_study2, fig.width=8, fig.height=4}
par(mfrow = c(1, 2))

plot(density(na.omit(qu2$Perf_Strivings)), 
     col = "blue", 
     main = "Perfectionistic Strivings", 
     xlab = "ZPS + ZSOP")

plot(density(na.omit(qu2$Perf_Concerns)), 
     col = "red", 
     main = "Perfectionistic Concerns", 
     xlab = "ZCM + ZDA + ZSPP")

```

```{r density_mood_scores_study2, fig.width=9, fig.height=10}
par(mfrow = c(3, 2))

plot(density(na.omit(qu2$POS_2)),
     col = "black",
     main = "Positive Mood: Pre-ABM",
     xlab = "Observed score (0–27)")

plot(density(na.omit(qu2$NEG_2)),
     col = "grey40",
     main = "Negative Mood: Pre-ABM",
     xlab = "Observed score (0–36)")

plot(density(na.omit(qu2$POS_3)),
     col = "black",
     main = "Positive Mood: Post-ABM / Pre-Tangram",
     xlab = "Observed score (0–27)")

plot(density(na.omit(qu2$NEG_3)),
     col = "grey40",
     main = "Negative Mood: Post-ABM / Pre-Tangram",
     xlab = "Observed score (0–36)")

plot(density(na.omit(qu2$POS_4)),
     col = "black",
     main = "Positive Mood: Post-Tangram",
     xlab = "Observed score (0–27)")

plot(density(na.omit(qu2$NEG_4)),
     col = "grey40",
     main = "Negative Mood: Post-Tangram",
     xlab = "Observed score (0–36)")
```

```{r mood_distribution_descriptives_study2}
round(psych::describe(qu2[c(
  "POS_2", "NEG_2", "POS_3", "NEG_3", "POS_4", "NEG_4"
)]), 2)
```

```{r density_etrt_study2, fig.width=8, fig.height=12}
par(mfrow = c(4, 2))

plot(density(na.omit(et_qu2$first_fix_prob_2)), 
     col='gold', 
     main='Probability of First or Second Fixation (t2)', 
     xlab ='')

plot(density(na.omit(et_qu2$first_fix_latency_2)), 
     col='orange', 
     main='Latency to First Fixation (t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_early_2)), 
     col='purple', 
     main='Dwell Time (Early, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_intermediate_2)),
     col='purple', 
     main='Dwell Time (Intermediate, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_late_2)), 
     col='purple', 
     main='Dwell Time (Late, t2)', 
     xlab = '')

plot(density(na.omit(et_qu2$dwell_time_2)), 
     col='purple', main='Dwell Time (t2)', 
     xlab = '')

plot(density(na.omit(rt_qu2$response_time_2)), 
     col='green', 
     main='Response Time (t2)', 
     xlab='')
```


\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# i) Model Inputs and Predictor Coding

## Semantic Coding

Semantic category was represented as the same five-level factor used in Study 1,
with Neutral specified as the reference category. For response-time models,
semantic category referred to the changed word; for eye-tracking models, it
referred to the AOI category. Planned `emmeans` comparisons tested emotional
valence, success versus failure, performance relevance, and non-neutral versus
neutral content following a supported omnibus interaction.

```{r semantic_class_rt_study2}
semantic_levels <- c("Neutral", "Positive", "Negative", "Success", "Failure")

rt_qu2$Change_category_f <- factor(
  rt_qu2$Change_category,
  levels = semantic_levels
)
stopifnot(levels(rt_qu2$Change_category_f)[1] == "Neutral")

# Planned comparisons among factor levels. Each vector is explicitly named to
# show the category mapping and uses the agreed integer coding.
semantic_planned <- list(
  # Negative minus positive, irrespective of performance relevance
  positive_vs_negative = c(
    Neutral = 0, Positive = -1, Negative = 1, Success = -1, Failure = 1
  ),
  # Failure minus success
  Success_Failure = c(
    Neutral = 0, Positive = 0, Negative = 0, Success = -1, Failure = 1
  ),
  # Performance-relevant minus performance-irrelevant
  performance_irrelevant_vs_relevant = c(
    Neutral = -2, Positive = -2, Negative = -2, Success = 3, Failure = 3
  ),
  # All non-neutral categories minus Neutral
  NonNeutral_vs_Neutral = c(
    Neutral = -4, Positive = 1, Negative = 1, Success = 1, Failure = 1
  )
)

stopifnot(
  all(vapply(semantic_planned, sum, numeric(1)) == 0),
  all(vapply(semantic_planned, function(x) identical(names(x), semantic_levels),
             logical(1)))
)
```

```{r semantic_class_et_study2}
et_qu2$IA_LABEL_f <- factor(
  et_qu2$IA_LABEL,
  levels = semantic_levels
)
stopifnot(levels(et_qu2$IA_LABEL_f)[1] == "Neutral")
```

## ABM Condition

ABM Condition was coded as a three-level factor (Control, Success, Failure), with the control condition as the reference category. Consequently, the condition coefficients and condition-by-semantic-category interaction coefficients compare failure- and success-oriented training with the control condition, which provides the intended test of each active training condition against sham training.

```{r abm_condition_study2}
qu2$Condition <- relevel(as.factor(qu2$Condition), ref = "Control")
rt_qu2$Condition <- relevel(as.factor(rt_qu2$Condition), ref = "Control")
et_qu2$Condition <- relevel(as.factor(et_qu2$Condition), ref = "Control")
stopifnot(
  levels(qu2$Condition)[1] == "Control",
  levels(rt_qu2$Condition)[1] == "Control",
  levels(et_qu2$Condition)[1] == "Control"
)
```

## Centering Predictors

Perfectionistic Strivings and Perfectionistic Concerns were mean-centered prior to analysis to reduce multicollinearity and facilitate interpretation.

```{r center_predictors_study2}
qu2$Perf_Strivings_c <- qu2$Perf_Strivings - mean(qu2$Perf_Strivings, na.rm = TRUE)
qu2$Perf_Concerns_c  <- qu2$Perf_Concerns  - mean(qu2$Perf_Concerns, na.rm = TRUE)

rt_qu2$Perf_Strivings_c <- rt_qu2$Perf_Strivings - mean(rt_qu2$Perf_Strivings, na.rm = TRUE)
rt_qu2$Perf_Concerns_c  <- rt_qu2$Perf_Concerns  - mean(rt_qu2$Perf_Concerns, na.rm = TRUE)

et_qu2$Perf_Strivings_c <- et_qu2$Perf_Strivings - mean(et_qu2$Perf_Strivings, na.rm = TRUE)
et_qu2$Perf_Concerns_c  <- et_qu2$Perf_Concerns  - mean(et_qu2$Perf_Concerns, na.rm = TRUE)
```

## Participant and Block Structure

The hierarchical structure followed the Study 1 analyses. All repeated-measures models included a participant random intercept. Eye-tracking models additionally included an uncorrelated participant-specific random slope for the target-AOI indicator where supported; latency models retained only the random intercept because the slope was not supported. A block-identity random intercept was considered but omitted from the primary models because it caused estimation problems for several outcomes and explained negligible variance where estimable. Eye-tracking models included mean-centered block presentation order as a fixed time covariate, whereas trial-level response-time models used mean-centered trial presentation order.

```{r smooth_terms_study2}
rt_qu2$subject_id_2 <- as.factor(rt_qu2$subject_id_2)
rt_qu2$subject_id_1 <- as.factor(rt_qu2$subject_id_1)
rt_qu2$block_id <- as.factor(rt_qu2$block_id)
rt_qu2$block_nr_1 <- as.integer(rt_qu2$block_nr_1)
rt_qu2$block_nr_2 <- as.integer(rt_qu2$block_nr_2)
rt_qu2$trial_nr_1 <- as.integer(rt_qu2$trial_nr_1)
rt_qu2$trial_nr_2 <- as.integer(rt_qu2$trial_nr_2)
rt_qu2$trial_nr_1_c <- rt_qu2$trial_nr_1 - mean(rt_qu2$trial_nr_1, na.rm = TRUE)
rt_qu2$trial_nr_2_c <- rt_qu2$trial_nr_2 - mean(rt_qu2$trial_nr_2, na.rm = TRUE)

et_qu2$subject_id_2 <- as.factor(et_qu2$subject_id_2)
et_qu2$subject_id_1 <- as.factor(et_qu2$subject_id_1)
et_qu2$block_id <- as.factor(et_qu2$block_id)
et_qu2$block_nr_1 <- as.integer(et_qu2$block_nr_1)
et_qu2$block_nr_2 <- as.integer(et_qu2$block_nr_2)
et_qu2$block_nr_c <- et_qu2$block_nr_2 - mean(et_qu2$block_nr_2, na.rm = TRUE)
```

For eye-tracking analyses, a binary indicator (Change_category01) was created to denote whether a given AOI matched the semantic category targeted by the change rule within a block (0 = non-target, 1 = target).

```{r change_category_study2}
et_qu2$Change_category <- as.factor(et_qu2$Change_category)

et_qu2$Change_category01 <- 0
et_qu2$Change_category01 <- as.integer(
  as.character(et_qu2$IA_LABEL) == as.character(et_qu2$Change_category)
)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# ii) Task Performance and Control Analysis

This section reports analyses assessing task performance over time and baseline equivalence across ABM conditions.

Given similar group sizes and the robustness of ANOVA to moderate violations of homogeneity of variance, no additional variance homogeneity tests were conducted for these control analyses.

## Task Performance

Paired-samples t-tests were conducted to examine pre–post changes in response accuracy and rule awareness.

```{r task_performance_tests_study2}
# Response accuracy
t.test(accuracy_1, accuracy_2, paired = TRUE)

# Rule awareness
t.test(rule_awareness_1, rule_awareness_2, paired = TRUE)
```

Response accuracy remained stable from T1 to T2, whereas rule awareness increased significantly over time, indicating improved detection of the semantic rule across blocks.

## Group Equivalence

One-way ANOVAs were conducted to assess equivalence across ABM conditions for task performance, perfectionism, and baseline psychological distress.

```{r group_equivalence_study2}
# Tangram performance
fit_Tangrams <- lm(Tangrams ~ Condition, data = qu2)
anova(fit_Tangrams)

# Perfectionism
fit_Strivings <- lm(Perf_Strivings ~ Condition, data = qu2)
anova(fit_Strivings)

fit_Concerns <- lm(Perf_Concerns ~ Condition, data = qu2)
anova(fit_Concerns)

# Baseline distress
fit_Depression <- lm(CESD ~ Condition, data = qu2)
anova(fit_Depression)

fit_Anxiety <- lm(GAD7 ~ Condition, data = qu2)
anova(fit_Anxiety)
```

No differences between ABM conditions were observed for Tangram performance, Perfectionistic Strivings or Perfectionistic Concerns, or baseline depressive and anxiety symptoms, indicating successful group equivalence.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# ii) Primary Manipulation Checks: Post-ABM Attention Conditional on Pre-ABM Attention

The manipulation checks tested whether the ABM conditions altered post-modification attentional allocation in the intended directions. Each post-ABM attentional measure was modeled conditional on its corresponding pre-ABM value. This baseline-adjusted formulation controls for pre-existing individual differences, preserves the measurement scale and distribution of each post-ABM outcome, and avoids incorporating baseline measurement error directly into a change score.

Eye-tracking models were estimated at the block-by-semantic-category level and included a participant random intercept and an uncorrelated participant-specific slope for `Change_category01`. Mean-centered block presentation order was included as a fixed time covariate. The trial-level response-time model included a participant random intercept and mean-centered trial presentation order. A block-identity random intercept was considered but omitted from the primary models because it produced singular or non-positive-definite solutions for several outcomes and explained negligible variance where estimable. `Change_category01` controlled whether the area of interest matched the semantic category targeted by the block rule. ABM condition was entered as a three-level factor with the control condition as the reference category; thus, all condition coefficients and condition-by-category coefficients compare failure- or success-oriented training with control.

Post-ABM eye-tracking proportions were analyzed using beta mixed-effects models with logit links. Values at 0 and 1 were moved slightly into the open unit interval before fitting. Post-ABM response times were analyzed using a gamma mixed-effects model with a log link because response times were strictly positive and right-skewed (Lo & Andrews, 2015). Rule awareness was included in each dispersion submodel. For every outcome, the manipulation check compared a model containing semantic category as a five-level factor with a model that added its interaction with ABM condition. Neutral stimuli were the reference category. The omnibus comparison evaluated whether the manipulation altered allocation across semantic categories; when supported, the factor coefficients directly characterized the category-specific differences from the reference category.

### Manipulation-Check Model Specification

For the beta eye-tracking outcomes, the mean submodel was:

\[
\begin{aligned}
g(\mu_{ij}) ={}& \beta_0 + \beta_1 Pre_{ij} + \sum_{k=1}^{4}\alpha_k C_{k,ij} + \sum_{h=1}^{2}\lambda_h Condition_{h,j} + \beta_2 BlockOrder_{ij} + \delta ChangeCategory_{ij} \\
&+ \sum_{k=1}^{4}\sum_{h=1}^{2}\gamma_{kh}(C_{k,ij}\times Condition_{h,j}) \\
&+ u_{0j} + u_{1j}ChangeCategory_{ij},
\end{aligned}
\]

where \(g(\cdot)\) is the logit link, \(Pre_{ij}\) is the corresponding pre-ABM attentional value, \(C_{k,ij}\) represents the four non-neutral semantic-category indicators, the two \(Condition_{h,j}\) indicators compare failure- and success-oriented training with control, and \(BlockOrder_{ij}\) is mean-centered block order. The beta precision submodel was:

\[
\log(\phi_{ij}) = \eta_0 + \eta_1 BR_{ij},
\]

where \(BR_{ij}\) denotes post-ABM rule awareness and larger \(\phi_{ij}\) indicates greater conditional precision.

For response time, the gamma mean submodel was:

\[
\begin{aligned}
\log(\mu_{ij}) ={}& \beta_0 + \beta_1 PreRT_{ij} + \sum_{k=1}^{4}\alpha_k C_{k,ij} + \sum_{h=1}^{2}\lambda_h Condition_{h,j} + \beta_2 TrialOrder_{ij} \\
&+ \sum_{k=1}^{4}\sum_{h=1}^{2}\gamma_{kh}(C_{k,ij}\times Condition_{h,j}) \\
&+ u_{0j},
\end{aligned}
\]

with dispersion submodel

\[
\log(\sigma_{ij}) = \eta_0 + \eta_1 BR_{ij}.
\]

Here, \(PreRT_{ij}\) is the corresponding pre-ABM response time, \(TrialOrder_{ij}\) is mean-centered trial order, and \(\sigma_{ij}\) is the gamma dispersion parameter.

The corresponding pre-ABM attentional value was mean-centered before model fitting. A centered value of zero therefore represents the sample-average pre-ABM value, and the estimated marginal means describe model-adjusted expected **post-ABM levels** for observations at that average baseline. Accordingly, active-condition-versus-control comparisons test whether the groups differ in adjusted post-ABM attentional allocation when compared at the same average pre-ABM level.

```{r prepare_primary_manipulation_checks_study2}
squeeze01_study2 <- function(x) {
  n <- sum(!is.na(x))
  ifelse(is.na(x), NA_real_, (x * (n - 1) + 0.5) / n)
}

mc_et2 <- et_qu2 %>%
  mutate(
    first_fix_prob_1_c = first_fix_prob_1 - mean(first_fix_prob_1, na.rm = TRUE),
    first_fix_latency_1_c = first_fix_latency_1 - mean(first_fix_latency_1, na.rm = TRUE),
    dwell_time_early_1_c = dwell_time_early_1 - mean(dwell_time_early_1, na.rm = TRUE),
    dwell_time_intermediate_1_c = dwell_time_intermediate_1 - mean(dwell_time_intermediate_1, na.rm = TRUE),
    dwell_time_late_1_c = dwell_time_late_1 - mean(dwell_time_late_1, na.rm = TRUE),
    dwell_time_1_c = dwell_time_1 - mean(dwell_time_1, na.rm = TRUE),
    first_fix_prob_2_t01 = squeeze01_study2(first_fix_prob_2),
    first_fix_latency_2_t01 = squeeze01_study2(first_fix_latency_2),
    dwell_time_early_2_t01 = squeeze01_study2(dwell_time_early_2),
    dwell_time_intermediate_2_t01 = squeeze01_study2(dwell_time_intermediate_2),
    dwell_time_late_2_t01 = squeeze01_study2(dwell_time_late_2),
    dwell_time_2_t01 = squeeze01_study2(dwell_time_2)
  )

mc_rt2 <- rt_qu2 %>%
  mutate(
    response_time_1_c = response_time_1 - mean(response_time_1, na.rm = TRUE)
  )
```

For outcomes with a supported omnibus interaction, the following helper first reports the difference between each active condition and control within each semantic category. It then reports the corresponding active-versus-control differences for the four planned theoretical contrasts. Because Condition and
semantic category are both factors, these follow-ups use estimated marginal means rather than `emtrends()`, which is reserved for slopes of continuous predictors. No follow-up table is produced when the omnibus interaction is not significant.

```{r manipulation_emmeans_helper_study2}
manipulation_emmeans_followup <- function(reduced, full, semantic_factor,
                                          alpha = .05) {
  model_comparison <- anova(reduced, full)
  p_column <- grep("^Pr\\(", names(model_comparison), value = TRUE)[1]
  omnibus_p <- model_comparison[[p_column]][2]

  if (is.na(omnibus_p) || omnibus_p >= alpha) {
    message("Omnibus interaction unsupported; follow-up comparisons omitted.")
    return(invisible(NULL))
  }

  category_formula <- as.formula(
    paste("~ Condition |", semantic_factor)
  )
  category_means <- emmeans(full, category_formula)
  category_condition_differences <- contrast(
    category_means,
    method = "trt.vs.ctrl",
    ref = "Control",
    by = semantic_factor,
    adjust = "none"
  )

  print(as.data.frame(summary(
    category_condition_differences,
    infer = c(TRUE, TRUE)
  )))

  semantic_formula <- as.formula(
    paste("~", semantic_factor, "| Condition")
  )
  semantic_means <- emmeans(full, semantic_formula)

  theoretical_by_condition <- contrast(
    semantic_means,
    method = semantic_planned,
    by = "Condition",
    adjust = "none"
  )

  theoretical_condition_differences <- contrast(
    update(theoretical_by_condition, by = "contrast"),
    method = "trt.vs.ctrl",
    ref = "Control",
    adjust = "none"
  )

  essential_table <- as.data.frame(summary(
    theoretical_condition_differences,
    infer = c(TRUE, TRUE)
  ))
  essential_table$omnibus_p <- omnibus_p
  essential_table$omnibus_supported <- TRUE

  essential_table
}
```

## Eye-Tracking Outcomes

### Probability of First or Second Fixation

```{r manipulation_check_first_fix_prob_study2}
mc_first_fix_prob_reduced <- glmmTMB(
  first_fix_prob_2_t01 ~
    first_fix_prob_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_first_fix_prob <- update(
  mc_first_fix_prob_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_first_fix_prob)
anova(mc_first_fix_prob_reduced, mc_first_fix_prob)
manipulation_emmeans_followup(
  mc_first_fix_prob_reduced, mc_first_fix_prob, "IA_LABEL_f"
)

```

### Latency to First Fixation

```{r manipulation_check_first_fix_latency_study2}
mc_first_fix_latency_reduced <- glmmTMB(
  first_fix_latency_2_t01 ~
    first_fix_latency_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_first_fix_latency <- update(
  mc_first_fix_latency_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_first_fix_latency)
anova(mc_first_fix_latency_reduced, mc_first_fix_latency)

```

### Dwell Time (Early Phase)

```{r manipulation_check_dwell_time_early_study2}
mc_dwell_time_early_reduced <- glmmTMB(
  dwell_time_early_2_t01 ~
    dwell_time_early_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_dwell_time_early <- update(
  mc_dwell_time_early_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_dwell_time_early)
anova(mc_dwell_time_early_reduced, mc_dwell_time_early)
manipulation_emmeans_followup(
  mc_dwell_time_early_reduced, mc_dwell_time_early, "IA_LABEL_f"
)

```

### Dwell Time (Intermediate Phase)

```{r manipulation_check_dwell_time_intermediate_study2}
mc_dwell_time_intermediate_reduced <- glmmTMB(
  dwell_time_intermediate_2_t01 ~
    dwell_time_intermediate_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_dwell_time_intermediate <- update(
  mc_dwell_time_intermediate_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_dwell_time_intermediate)
anova(mc_dwell_time_intermediate_reduced, mc_dwell_time_intermediate)
manipulation_emmeans_followup(
  mc_dwell_time_intermediate_reduced, mc_dwell_time_intermediate, "IA_LABEL_f"
)

```

### Dwell Time (Late Phase)

```{r manipulation_check_dwell_time_late_study2}
mc_dwell_time_late_reduced <- glmmTMB(
  dwell_time_late_2_t01 ~
    dwell_time_late_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_dwell_time_late <- update(
  mc_dwell_time_late_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_dwell_time_late)
anova(mc_dwell_time_late_reduced, mc_dwell_time_late)
manipulation_emmeans_followup(
  mc_dwell_time_late_reduced, mc_dwell_time_late, "IA_LABEL_f"
)

```

### Dwell Time (Whole Trial)

```{r manipulation_check_dwell_time_whole_study2}
mc_dwell_time_reduced <- glmmTMB(
  dwell_time_2_t01 ~
    dwell_time_1_c + Condition +
    IA_LABEL_f +
    block_nr_c + Change_category01 + 
    #(1 | block_id) + 
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_et2,
  na.action = na.omit
)

mc_dwell_time <- update(
  mc_dwell_time_reduced,
  . ~ . + IA_LABEL_f:Condition
)

summary(mc_dwell_time)
anova(mc_dwell_time_reduced, mc_dwell_time)
manipulation_emmeans_followup(
  mc_dwell_time_reduced, mc_dwell_time, "IA_LABEL_f"
)

```

## Response Time

```{r manipulation_check_response_time_study2}
mc_response_time_reduced <- glmmTMB(
  response_time_2 ~
    response_time_1_c + Condition +
    Change_category_f + trial_nr_2_c + 
    #(1 | block_id) + 
    (1 | subject_id_2),
  REML = FALSE,
  family = Gamma(link = "log"),
  dispformula = ~ guessed_block_rule_2,
  data = mc_rt2,
  na.action = na.omit
)

mc_response_time <- update(
  mc_response_time_reduced,
  . ~ . + Change_category_f:Condition
)

summary(mc_response_time)
anova(mc_response_time_reduced, mc_response_time)
manipulation_emmeans_followup(
  mc_response_time_reduced, mc_response_time, "Change_category_f"
)

```

# iii) Primary TPIS-Informed Analysis: Moderation of Perfectionism–Mood Associations

The primary analysis examined whether **ABM condition moderated the relationship between perfectionism and post-Tangram mood**, adjusting for mood immediately before the Tangram task. 

Positive mood at both intervals and negative mood immediately after ABM were analyzed using ordinary Gaussian linear models with identity links because their distributions did not show substantial skew. Post-Tangram negative mood was analyzed using a single-level Tweedie model with a log link because it was more clearly right-skewed and included meaningful zero scores. For this outcome, a score of zero represented the plausible substantive state of no endorsed negative emotion rather than an inadmissible or incidental boundary value. A gamma distribution was therefore unsuitable because it requires strictly positive outcomes. With its estimated power parameter constrained between 1 and 2, the compound Poisson-gamma Tweedie distribution accommodates both a probability mass at zero and a continuous positive distribution (Dunn & Smyth, 2005).

Nested Gaussian linear models were compared using omnibus *F* tests, and the nested post-Tangram negative-mood Tweedie models were compared using a likelihood-ratio test. The condition-by-perfectionism interaction was the principal TPIS-informed test; it should not be interpreted as a conventional estimated mediation path or indirect effect.

Two sets of analyses were conducted:

- **Control analyses:** post-ABM mood, adjusted for pre-ABM mood  
- **Main analyses:** post-Tangram mood, adjusted for pre-Tangram mood (i.e., mood immediately after ABM)

All models included:

- **Perfectionistic Strivings** and **Perfectionistic Concerns**
- **ABM condition**
- the interaction terms between perfectionism and ABM condition
- **baseline depressive symptoms (CES-D)** and **baseline anxiety symptoms (GAD-7)** as covariates

ABM condition was treated as a categorical predictor, with additional releveling used in follow-up models to decompose significant interactions.

## Model Specification

### General Model

\[
PostMood_j =
\beta_0
+ \beta_1 PreMood_j
+ \beta_2 PS_j
+ \beta_3 PC_j
+ \beta_4 Cond_j
+ \beta_5 (PS_j \times Cond_j)
+ \beta_6 (PC_j \times Cond_j)
+ \beta_7 CESD_j
+ \beta_8 GAD7_j
+ \varepsilon_j
\]

where:

- \(PostMood_j\): the relevant post-assessment positive- or negative-mood composite for participant \(j\)
- \(PreMood_j\): the corresponding mood composite at the immediately preceding assessment
- \(PS_j\): Perfectionistic Strivings for participant \(j\)
- \(PC_j\): Perfectionistic Concerns for participant \(j\)
- \(Cond_j\): ABM condition (Control, Success, Failure)
- \(CESD_j\): baseline depressive symptoms
- \(GAD7_j\): baseline anxiety symptoms
- \(\varepsilon_j\): residual error

Because these models were estimated at the participant level, no random effects were included. Coefficients from the Gaussian positive-mood and post-ABM negative-mood models are expressed in raw mood-score units. The log-linked post-Tangram negative-mood model expresses effects multiplicatively, so its predicted values should be interpreted on the response scale.

## Control Analyses: Post-ABM Mood Conditional on Pre-ABM Mood

These analyses tested whether ABM condition was associated with post-ABM mood after accounting for pre-ABM mood, before the failure induction.

### Post-ABM Positive Mood

**1. Post-ABM Positive Mood (adjusted for pre-ABM positive mood)**

```{r lm0.1_positive}
mood_post_abm_positive_cc <- qu2 %>%
  filter(complete.cases(POS_3, POS_2, Perf_Strivings_c,
                        Perf_Concerns_c, Condition, CESD, GAD7))

stopifnot(all(mood_post_abm_positive_cc$POS_3 >= 0))

lm0.1_positive <- lm(
  POS_3 ~ POS_2 + 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7,
  data = mood_post_abm_positive_cc
)
summary(lm0.1_positive)
lm0.1_positive_reduced <- update(
  lm0.1_positive,
  . ~ . - Perf_Strivings_c:Condition - Perf_Concerns_c:Condition
)
anova(lm0.1_positive_reduced, lm0.1_positive)
```

### Post-ABM Negative Mood

**2. Post-ABM Negative Mood (adjusted for pre-ABM negative mood)**

```{r lm0.2_negative}
mood_post_abm_negative_cc <- qu2 %>%
  filter(complete.cases(NEG_3, NEG_2, Perf_Strivings_c,
                        Perf_Concerns_c, Condition, CESD, GAD7))

lm0.2_negative <- lm(
  NEG_3 ~ NEG_2 + 
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7,
  data = mood_post_abm_negative_cc
)
summary(lm0.2_negative)
lm0.2_negative_reduced <- update(
  lm0.2_negative,
  . ~ . - Perf_Strivings_c:Condition - Perf_Concerns_c:Condition
)
anova(lm0.2_negative_reduced, lm0.2_negative)
```

## Main Analyses: Post-Tangram Mood Conditional on Pre-Tangram Mood

These models tested whether ABM condition moderated the relationship between perfectionism and post-Tangram mood after accounting for mood immediately before the failure induction.

Separate complete-case datasets were created for the two outcomes.

```{r mood_complete_cases_study2}
mood_positive_cc <- qu2 %>%
  filter(complete.cases(POS_4, POS_3, Perf_Strivings_c,
                        Perf_Concerns_c, Condition, CESD, GAD7))

mood_negative_cc <- qu2 %>%
  filter(complete.cases(NEG_4, NEG_3, Perf_Strivings_c,
                        Perf_Concerns_c, Condition, CESD, GAD7))

stopifnot(all(mood_positive_cc$POS_4 >= 0),
          all(mood_negative_cc$NEG_4 >= 0))
```

### Positive Mood

**3. Post-Tangram Positive Mood (adjusted for pre-Tangram positive mood)**

```{r lm1.1_positive_study2}
lm1.1_positive <- lm(
  POS_4 ~ POS_3 +
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7,
  data = mood_positive_cc
)

lm1.1_positive_reduced <- update(
  lm1.1_positive,
  . ~ . - Perf_Strivings_c:Condition - Perf_Concerns_c:Condition
)

summary(lm1.1_positive)
anova(lm1.1_positive_reduced, lm1.1_positive)
```

### Negative Mood

**4. Post-Tangram Negative Mood (adjusted for pre-Tangram negative mood)**

The Gaussian and Tweedie models below use the same outcome, analytic sample, and predictor structure. Because they differ in their assumed outcome distributions and are not nested, their relative fit is compared using AIC rather than a likelihood-ratio test. Residual diagnostics are also shown for both candidate models.

```{r lm1.2_negative_gaussian_study2}
lm1.2_negative_gaussian <- lm(
  NEG_4 ~ NEG_3 +
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7,
  data = mood_negative_cc
)

lm1.2_negative_gaussian_reduced <- update(
  lm1.2_negative_gaussian,
  . ~ . - Perf_Strivings_c:Condition - Perf_Concerns_c:Condition
)

summary(lm1.2_negative_gaussian)
anova(lm1.2_negative_gaussian_reduced, lm1.2_negative_gaussian)
```

```{r glm1.2_negative_tweedie_study2}
glm1.2_negative <- glmmTMB(
  NEG_4 ~ NEG_3 +
    Perf_Strivings_c * Condition +
    Perf_Concerns_c * Condition +
    CESD + GAD7,
  REML = FALSE,
  family = tweedie(link = "log"),
  data = mood_negative_cc
)

glm1.2_negative_reduced <- update(
  glm1.2_negative,
  . ~ . - Perf_Strivings_c:Condition - Perf_Concerns_c:Condition
)

summary(glm1.2_negative)
anova(glm1.2_negative_reduced, glm1.2_negative, test = "Chisq")
```

```{r lm1.2_glm1.2_model_comparison}
negative_mood_family_aic <- AIC(
  lm1.2_negative_gaussian,
  glm1.2_negative
)
rownames(negative_mood_family_aic) <- c("Gaussian", "Tweedie")
negative_mood_family_aic
```


```{r post_tangram_negative_family_diagnostics, fig.width = 10, fig.height = 8}
family_comparison_models <- list(
  "Gaussian" = lm1.2_negative_gaussian,
  "Tweedie" = glm1.2_negative
)

par(mfrow = c(2, 2))
for (model_name in names(family_comparison_models)) {
  model <- family_comparison_models[[model_name]]
  pearson_residuals <- residuals(model, type = "pearson")
  plot(
    fitted(model), pearson_residuals,
    xlab = "Fitted negative mood", ylab = "Pearson residuals",
    main = paste(model_name, "residuals")
  )
  abline(h = 0, lty = 2)
  qqnorm(pearson_residuals, main = paste(model_name, "Q-Q plot"))
  qqline(pearson_residuals)
}
```

### Distributional Model Diagnostics

The following plots examine residual patterns from the best-supported nested model for each mood outcome and interval. Both positive-mood models and the post-ABM negative-mood model use the Gaussian family; the post-Tangram negative-mood model uses the Tweedie family. The full interaction model is used only when it significantly improves fit over its reduced counterpart.

```{r mood_diagnostics_study2, fig.width = 10, fig.height = 14}
select_supported_model <- function(reduced, full, alpha = .05) {
  comparison <- anova(reduced, full)
  p_column <- grep("^Pr\\(", names(comparison), value = TRUE)
  p_value <- comparison[[p_column[1]]][2]
  if (!is.na(p_value) && p_value < alpha) full else reduced
}

mood_diagnostic_models <- list(
  "Post-ABM positive mood" = select_supported_model(
    lm0.1_positive_reduced, lm0.1_positive
  ),
  "Post-ABM negative mood" = select_supported_model(
    lm0.2_negative_reduced, lm0.2_negative
  ),
  "Post-Tangram positive mood" = select_supported_model(
    lm1.1_positive_reduced, lm1.1_positive
  ),
  "Post-Tangram negative mood" = select_supported_model(
    glm1.2_negative_reduced, glm1.2_negative
  )
)

par(mfrow = c(4, 2))
for (model_name in names(mood_diagnostic_models)) {
  model <- mood_diagnostic_models[[model_name]]
  pearson_residuals <- residuals(model, type = "pearson")
  plot(
    fitted(model), pearson_residuals,
    xlab = "Fitted mood", ylab = "Pearson residuals",
    main = model_name
  )
  abline(h = 0, lty = 2)
  qqnorm(pearson_residuals, main = paste(model_name, "Q-Q plot"))
  qqline(pearson_residuals)
}
```

**Interaction plots**

Only interactions meeting both criteria--a significant omnibus model comparison and a significant individual interaction--are plotted. In the current results, this rule supports plotting the interaction of Perfectionistic Strivings with ABM condition for post-Tangram negative mood only. All lines are solid; the failure-condition line is thicker and shown at full opacity because the Strivings-by-Failure versus Control coefficient was significant, whereas the control and success lines are thinner and lighter. This visual emphasis does not imply that the within-condition Strivings slope was separately tested or significant.

```{r lm1.2_interaction_plot_study2, fig.width=7, fig.height=4}
pred_neg_ps <- ggpredict(
  glm1.2_negative,
  terms = c("Perf_Strivings_c [all]", "Condition"),
  type = "fixed"
)

pred_neg_ps_data <- as.data.frame(pred_neg_ps) %>%
  mutate(
    group = factor(as.character(group), levels = c("Control", "Success", "Failure")),
    supported = as.character(group) == "Failure"
  )
stopifnot(
  !anyNA(pred_neg_ps_data$group),
  setequal(as.character(unique(pred_neg_ps_data$group)),
           c("Control", "Success", "Failure"))
)

ip_neg_1 <- ggplot(
  pred_neg_ps_data,
  aes(x = x, y = predicted, group = group, color = group,
      linewidth = supported, alpha = supported)
) +
  geom_line() +
  scale_color_manual(values = c(
    Control = "#000000",
    Success = "#0072B2",
    Failure = "#D55E00"
  ), breaks = c("Control", "Success", "Failure"),
  labels = c("Control", "Success", "Failure"), drop = FALSE) +
  scale_linewidth_manual(values = c(`FALSE` = 0.65, `TRUE` = 1)
                         , guide = "none"
                         ) +
  scale_alpha_manual(values = c(`FALSE` = 0.65, `TRUE` = 1)
                     , guide = "none"
                     ) +
  labs(
    title = "Predicted negative mood following the Tangram task",
    x = "Perfectionistic Strivings",
    y = NULL,
    color = "ABM condition"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )

ip_neg_1
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# iv) Secondary Process-Verification Analysis

This secondary analysis examined whether ABM condition moderated the category-specific association between Perfectionistic Concerns and intermediate dwell time that was supported in Study 1, remained supported after controlling for depressive and anxiety symptoms, and was also observed at T1 in the Study 2 sample. The analysis therefore provides a targeted process-verification test
rather than an additional manipulation check or a conventional mediation test.

Post-ABM intermediate dwell time was modeled conditional on centered pre-ABM intermediate dwell time. The reduced model included the two-way associations among semantic category, Perfectionistic Concerns, and ABM condition, together
with the same fixed covariates, random-effects structure, and dispersion submodel used in the corresponding manipulation check. The full model added the targeted three-way interaction among the negative-versus-neutral category comparison, Perfectionistic Concerns, and ABM condition. 

The models were compared using a likelihood-ratio test. Because this omnibus comparison is the process-verification test, individual higher-order coefficients are not interpreted when the full model does not improve fit.

```{r secondary_process_verification_study2}
process_mc_et2 <- mc_et2 %>%
  mutate(
    IA_Negative_vs_Neutral = as.numeric(IA_LABEL_f == "Negative")
  )

process_intermediate_reduced <- glmmTMB(
  dwell_time_intermediate_2_t01 ~ dwell_time_intermediate_1_c +
    IA_LABEL_f * Perf_Concerns_c + IA_LABEL_f * Condition +
    Perf_Concerns_c * Condition + block_nr_c + Change_category01 +
    # (1 | block_id) +
    (1 + Change_category01 || subject_id_2),
  REML = FALSE,
  family = beta_family(link = "logit"),
  dispformula = ~ guessed_block_rule_2,
  data = process_mc_et2,
  na.action = na.omit
)

process_intermediate_full <- update(
  process_intermediate_reduced,
  . ~ . + IA_Negative_vs_Neutral:Perf_Concerns_c:Condition
)

summary(process_intermediate_full)
anova(process_intermediate_reduced, process_intermediate_full)
```

The targeted three-way interaction did not significantly improve model fit.
Accordingly, the individual higher-order coefficients were not interpreted, and this analysis did not provide evidence that ABM condition modified the negative-versus-neutral intermediate-dwell-time association with
Perfectionistic Concerns.

# Reference

Brooks, M. E., Kristensen, K., van Benthem, K. J., Magnusson, A., Berg, C. W., Nielsen, A., Skaug, H. J., Mächler, M., & Bolker, B. M. (2017). glmmTMB balances speed and flexibility among packages for zero-inflated generalized linear mixed modeling. *The R Journal, 9*(2), 378–400. <https://doi.org/10.32614/RJ-2017-066>

Dunn, P. K., & Smyth, G. K. (2005). Series evaluation of Tweedie exponential dispersion model densities. *Statistics and Computing, 15*(4), 267–280. <https://doi.org/10.1007/s11222-005-4070-y>

Lo, S., & Andrews, S. (2015). To transform or not to transform: Using
generalized linear mixed models to analyse reaction time data. Frontiers
in Psychology, 6, Article 1171.
<https://doi.org/10.3389/fpsyg.2015.01171> 
